---
title: "Analysis of simulation results of pension risk-sharing"
output: 
  html_notebook: 
    number_sections: yes
    toc: yes
    fig_caption: yes
editor_options: 
  chunk_output_type: console
---


# Notes

Notes on measures
https://docs.google.com/document/d/1oi2UEfcrsk6359-zbJTb8DamtbpoEGUFLzcY19njwUI/edit


**Comparing distributions of results from two policy scenarios**

For summary variables that each sim corresponds to a single value (eg. PV ERC, PV benefit)

1. Sim-to-sim comparisons. Calculate sim-to-sim differences for each sim then examine:
 - Order the differences by an external variable (eg. variable values in baseline, compound return), then present the quantiles
 - Order the differences by an external variable (eg. variable values in baseline, compound return), and divide them into serveral groups, then present the median/mean of each group.  
 - Order the differences themselves and present the quantiles.  

2. Comparing the distributions (percentiles) of these variables (no differences taken) 


TODO re 05/26 call

- Results for benefits
- Results for trade-off
- discussion on contribution

- Risk-measures
- Modeling method
- examples in result section

- Clean up tables and figures. 
- Deterministic asset shock scenario


- max 5-year contribution in 10~20 years
- Examples when explaining tables
- label return groups
- levels of titles
- summary table: explain dots in the table

- deterministic run
- better way to deal with policy labels

- Later:
  - Benefit analysis: using an individual as example (year of death known?)
  - Show upside and downside risks, eg EEC_return policies 
  - check contingent EEC policies, 
     - EEC return: use 5/10-year average return, instead of single year return. 




```{r Global_settings, include=FALSE}

## Loading packages
source(here::here("libraries.R"))

theme_set(theme_yy())

dir_modelResults <- paste0(here::here(),"/Outputs/")
# dir_modelResults <- paste0(here::here(),"/Outputs_500sims/")
dir_outputs      <- paste0(here::here(),"/Outputs_Analysis/") 


# Global parameters for analysis
dr     <- 0.075 # discount rate
dr_low <- 0.03  # lower discount rate
infl  <- 0.02  # assumed inflation rate
Nyear <- 40    # Number of sim years for contribution analysis
cola_baseline <- 0.015

DC_EECrate <- 0.025
DC_ERCrate <- 0.028

# run names for policy runs to show in results 
# policy_select <- c("baseline", "cola_return", "cola_FR", "EEC_sharedADCfloor", "EEC_return", "EEC_FR", "hybrid_DB")
runnames_show1 <- c("baseline", 
										
										"cola_return", 
										"cola_FR", 
							
										"EEC_return", 
										"EEC_FR"
										# "EEC_sharedADCfloor"
										
										#"hybrid_DB"
										)

runnames_show1_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA:\nReturn",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_FR             = "Contingent EEC:\nFunded ratio"
)
	
	


runnames_show2 <- c("baseline", 
										
										"cola_return", 
										
										"cola_FR",
										"cola_FR_FR100"
										
										#"cola_FRramp",
										#"cola_FRramp_FR100"
										)


runnames_show2_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA: \n return",
	cola_FR            = "Contingent COLA: \n Funded ratio\nYear-1 funded ratio 75%",
  cola_FR_FR100      = "Contingent COLA: \n Funded ratio\nYear-1 funded ratio 100%"
)


```

```{r Loading_results, include = FALSE}

source(here::here("Analysis_loadingResults.R"))
# Outputs: 
   # results_all
   # run_labels


```


# Analysis of ERC

 
**Q1. Overall cost reduction effects** 

**Question**: How large are the cost-reducing effects of common risk-sharing policies? What are the factors that affect the cost-reducing effects?

**Measures:**

1. Sim-to-sim differences between PVC under baseline and PVC under risk sharing policy (40-year) at percentiles of baseline PVC. Calculate the differences in PVC for each of the 2,000 simulations, and present the results at 5 percentiles of the baseline PVC (can be presented as differences in normalized dollar values or differences percentage).


2. [MFC]Median sim-to-sim differences between PVC under baseline and PVC under risk sharing policy (40-year) in groups of 40-year compound return. Calculate the differences in PVC for each of the 2,000 simulations, and present average differences within 5 groups of 40-year CAGR. (can be presented as differences in normalized dollar values or differences percentage). 

3. Percentiles of the differences from baseline WITHIN each policy (the same row does not correspond to the same sim or group)

4. [MFC]Percentiles of the PVC under each policy. This measure is NOT a sim-to-sim comparison, but a comparison of PVC distributions. (distribution of differences vs. difference in distributions.)

**Discussion of the measures**

- As measure 1 is based the cost differences of single sims, the results can show patterns that are difficult to interpret. For example, the cost cost differences (dollar and %) are not always increasing when moving from lower percetiles to higher percentiles of baseline PV ERC. This is perhaps because (1) the order of baseline PV ERC cannot capture the overall effect of all factors (eg. overall return; volatility) that affect cost-savings (the impact of individual factors may not follow the same order of PV ERC), (2) the randomness of the results. A further question is: do the "irregularities" observed in the results represent some "patterns" that is worth further examination, or just pure randomness? (TODO: plot all 2,000 PVC differences against arranged in the order of baseline PVC).   
- The reseults of measure 2 is more consistent with our expectation: the lower the 40-year return, the higher ERC savings  


**Key results**

- Note: For now, mostly based on measure 2, which is easier to interpret.

- The contingent COLA policies examined provide moderate overall cost reduction effects (-4% to -10%), with the FR-based COLA policy being more responsive to the long-tern return environment and can provide meaningful cost savings low return environment: the cost-reduction is more than 10% in the worst long-term return group (10th percentile and below), compared to 6.7% of the return-based COLA.    

- The impacts on PVC of the return-based and FR-based EEC policies are quite limited.(-2% ~ +4%), with the FR-based policy being a bit more responsive to long-tern returns. Note that these policies can lead to higher employer costs in good return scenarios as the EEC rates can fall below the base level (fixed EEC rate in baseline).

- The shared-ADC policy has far stronger cost-reduction effect than other policies, reducing PV ERC by about 1/3 in all long-term return groups.   


<br><br/>


**Q2: Dampening effects on asset shock**

**Question**: To what extent risk-sharing policies can dampen the impact of large asset shocks on contributions?

There are two aspects to this question

**Measures**

1. [MFC] Probability of ERC rate rising by more than 10 percentage points within 5 years. This measures the the likelihood of large increases of ERC
2. [MFC] Max increase in ERC rate in 5 years. This measures the strength of the buffering effects when asset shock occurs.  
3. Measure based on sim-to-sim comparison of ERC rate between baseline and risk-sharing policies 
4. (TODO) Examine ERC rate under a deterministic asset shock scenario similar to the Great Recession. This can help put the results in context.   

**Key results**

- As measured by the first two measures, the volatility dampening effects of the contingent COLA and EEC policies  are quite small. In fact, the return-based contingent EEC policy leads to higher contribution volatility. (But we should note that the conclusion may depend on how contribution volatility is defined and measured) 

- Measure 3 shows that annual ERC rate can be reduced by 2~4 percentage points under the contingent COLA policies and 1~2 percentage points under the the two contingent EEC policies.(TODO: show the corresponding ERC rate in baseline)  

- The shared-ADC policy can significantly reduce ERC volatility(much lower prob of large increases of ERC rate, much lower max 5-year ERC rate change, much greater reduction in annual ERC rate in bad years)

- TODO: show deterministic asset shock scenario. 

- Under the current measures 1-3, the dempening effects on contribution volatility are quite limited.





<br><br/>

**Notes**

* Only look at runs starting with 75% funded ratio
* The parameters of the risk-sharing policies affect the impacts of these policies. For each policy, have two runs with different risk-sharing parameters and compare the results.  
* Only present 1~3 measures for each question, can put other measures in appendix if necessary.  


```{r ERC_prep, echo = FALSE, warning=FALSE}

results_stch_FR75 <-  
  results_all %>% 
	filter(!str_detect(runname, "FR100")) %>% 
	# filter(sim >= 1, year %in% 21:40) 
	filter(sim >= 1, year <= Nyear) 


# results_stch_FR100 <-  
#   results_all %>% 
# 	filter(str_detect(runname, "FR100")) %>% 
# 	filter(sim >= 1, year <= Nyear) 


## PV ERC and EEC 
df_PVC <- 
  results_stch_FR75 %>% 
	select(runname, runname_wlabel, sim, year, policy_type, ERC, EEC, UAAL) %>% 
	group_by(runname, sim) %>% 
	summarise(
		        runname_wlabel = unique(runname_wlabel),
						
		        # PV of ERC
		        ERC_PV         = sum(ERC / (1 + dr)^(year - 1)),
						ERCwUAAL_PV    = sum(ERC / (1 + dr)^(year - 1)) + UAAL[year == max(year)] / (1 + unique(dr))^(max(year) - 1),
						
						# PV of EEC
						EEC_PV         = sum(EEC / (1 + dr)^(year - 1))
						)
# df_PVC

## Percentiles of PVC for each policy
df_PVC_qtiles <- 
	df_PVC %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						ERC_PV_q90 = quantile(ERC_PV, 0.90),
						ERC_PV_q75 = quantile(ERC_PV, 0.75),
						ERC_PV_q50 = quantile(ERC_PV, 0.50),
						ERC_PV_q25 = quantile(ERC_PV, 0.25),
						ERC_PV_q10 = quantile(ERC_PV, 0.1),
						
						ERCwUAAL_PV_q90 = quantile(ERCwUAAL_PV, 0.90),
						ERCwUAAL_PV_q75 = quantile(ERCwUAAL_PV, 0.75),
						ERCwUAAL_PV_q50 = quantile(ERCwUAAL_PV, 0.50),
						ERCwUAAL_PV_q25 = quantile(ERCwUAAL_PV, 0.25),
						ERCwUAAL_PV_q10 = quantile(ERCwUAAL_PV, 0.1),
						
						EEC_PV_q90 = quantile(EEC_PV, 0.90),
						EEC_PV_q75 = quantile(EEC_PV, 0.75),
						EEC_PV_q50 = quantile(EEC_PV, 0.50),
						EEC_PV_q25 = quantile(EEC_PV, 0.25),
						EEC_PV_q10 = quantile(EEC_PV, 0.1)
						)

# df_PVC_qtiles
# Why PV ERC of SDRS is so low, even with final UAAL?





# Sim-to-sim comparison of PVC at the same percentile PVC under baseline 

# find the sim# corresponding to percentiles of PVC under the baseline policy
ptiles_measure <- c(ptile90 = 0.9, ptile75 = 0.75, ptile50 = 0.50, ptile25 = 0.25, ptile10 = 0.1)
nsim <- filter(df_PVC, runname == "baseline") %>% nrow()

df_PVC_sim2sim <- 
df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	spread(runname, ERC_PV) %>% 
	arrange(desc(baseline)) %>% 
	mutate(sim_rank = 1:nsim) %>% 
	filter(sim_rank %in% round(nsim*ptiles_measure)) %>% 
	mutate(Percentile = names(ptiles_measure),
				 var = "ERC_PV") %>% 
	select(var, Percentile, everything(), -sim, -sim_rank)
	

# Grouping variables

## Grouping by 40-year compound return 

# Dividing simulations into 5 groups based 40-year CAGR, difference in ERC rate:
#    1) 90th percentile and above []
#    2) 75th~90th percentile [)
#    3) 25th~75th percentile [)
#    4) 25th percentile and below [)
# Grouping can be done based on other variables (e.g. std of return)

df_CAGR40 <- 
results_all %>% 
	filter(runname == "baseline", sim >= 1) %>% 
	group_by(sim) %>% 
	summarise(CAGR40 = get_geoReturn(i.r)) 
  #summarise(CAGR40 = sd(i.r)) 

grpVals_CAGR40 <-
	df_CAGR40 %>% 
	summarise(CAGR40_pinf= Inf,
		        CAGR40_q90 = quantile(CAGR40, 0.80),
						CAGR40_q75 = quantile(CAGR40, 0.60),
						CAGR40_q50 = quantile(CAGR40, 0.50),
						CAGR40_q25 = quantile(CAGR40, 0.40),
						CAGR40_q10 = quantile(CAGR40, 0.20),
						CAGR40_ninf= -Inf,
	) 

#unlist(grpVals_CAGR40[1,])[-4] 
#df_CAGR40$CAGR40
#cut(df_CAGR40$CAGR40, unlist(grpVals_CAGR40[1,])[-4], label = F )

grpVals_CAGR40_vector <- unlist(grpVals_CAGR40[1,2:6])

df_CAGR40 %<>% 
	mutate(
		grp_CAGR40 = cut(CAGR40, unlist(grpVals_CAGR40[1,])[-4], label = F )
		# grp_CAGR40 = case_when(
		# CAGR40 >= grpVals_CAGR40$CAGR40_q90 ~ 1,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q75 & CAGR40 < grpVals_CAGR40$CAGR40_q90 ~ 2,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q25 & CAGR40 < grpVals_CAGR40$CAGR40_q75 ~ 3,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q10 & CAGR40 < grpVals_CAGR40$CAGR40_q25 ~ 4,
		# CAGR40 < grpVals_CAGR40$CAGR40_q10 ~ 5,
		# TRUE ~ NA_real_) 
	)


grp_CAGR40_labels <- c(
	"< 6.5%",
  "6.5%~7.2%",
  "7.2%~7.9%",
  "7.9%~8.6%",
  "> 8.6%"
)


# Grouping by standard deviation
df_SD_return <- 
results_all %>% 
	filter(runname == "baseline", sim >= 1) %>% 
	group_by(sim) %>% 
	summarise(SD_return = sd(i.r)) 

grpVals_SD_return <-
	df_SD_return %>% 
	summarise(SD_return_pinf= Inf,
		        SD_return_q90 = quantile(SD_return, 0.80),
						SD_return_q75 = quantile(SD_return, 0.60),
						SD_return_q50 = quantile(SD_return, 0.50),
						SD_return_q25 = quantile(SD_return, 0.40),
						SD_return_q10 = quantile(SD_return, 0.20),
						SD_return_ninf= -Inf,
	) 

#unlist(grpVals_CAGR40[1,])[-4] 
#df_CAGR40$CAGR40
#cut(df_CAGR40$CAGR40, unlist(grpVals_CAGR40[1,])[-4], label = F )

grpVals_SD_return_vector <- unlist(grpVals_SD_return[1,2:6])

df_SD_return %<>% 
	mutate(
		grp_SD_return = cut(SD_return, unlist(grpVals_SD_return[1,])[-4], label = F )
		# grp_CAGR40 = case_when(
		# CAGR40 >= grpVals_CAGR40$CAGR40_q90 ~ 1,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q75 & CAGR40 < grpVals_CAGR40$CAGR40_q90 ~ 2,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q25 & CAGR40 < grpVals_CAGR40$CAGR40_q75 ~ 3,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q10 & CAGR40 < grpVals_CAGR40$CAGR40_q25 ~ 4,
		# CAGR40 < grpVals_CAGR40$CAGR40_q10 ~ 5,
		# TRUE ~ NA_real_) 
	)


# df_CAGR40

## Measure 3, distributions(percenties of differences)

df_PVC_sim2sim_m3 <- 
	df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	left_join(filter(df_PVC, runname == "baseline") %>% ungroup() %>%  select(sim, ERC_PV_baseline = ERC_PV), by = "sim") %>% 
	mutate(diff_ERC_PV     = ERC_PV -  ERC_PV_baseline,
				 diff_ERC_PV_pct = 100* (ERC_PV / ERC_PV_baseline - 1)) %>% 
	group_by(runname) %>% 
	summarise(
		dff_ERC_PV_pct_q90 = quantile(diff_ERC_PV_pct, 0.90),
	  dff_ERC_PV_pct_q75 = quantile(diff_ERC_PV_pct, 0.75),
	  dff_ERC_PV_pct_q50 = quantile(diff_ERC_PV_pct, 0.50),
	  dff_ERC_PV_pct_q25 = quantile(diff_ERC_PV_pct, 0.25),
	  dff_ERC_PV_pct_q10 = quantile(diff_ERC_PV_pct, 0.10)
		) %>% 
	gather(Percentile, value, -runname) %>% 
	spread(runname, value) 

# df_PVC_sim2sim.2 



## Measure 4 






## Maximum increase in ERC rate WITHIN 5 years

# Note:
#  - Need to take into account the possibility that the changes in less then 5 years
#    are greater than the 5-year change. The method below takes care of this. 

# x <- filter(results_stch, sim ==1, runname == "cola_baseline") %>% pull("ERC_PR")
# zoo::rollapply(x, width = 6, get_nyearMax, fill = NA, align = "right")


df_ERCMaxChg <- 
	results_stch_FR75 %>% 
	select(runname, runname_wlabel, sim, year, policy_type, ERC_PR) %>%
	group_by(runname, sim) %>% 
	mutate(   ERC_PR_chg5y    = rollapply(ERC_PR, width = 6, get_nyearMax, fill = NA, align = "right")) %>% # zoo::rollapply
	summarise(runname_wlabel = unique(runname_wlabel),
		        ERC_PR_chg5yMax = max(ERC_PR_chg5y, na.rm = TRUE))

# df_ERCMaxChg


df_ERCMaxChg_qtile <- 
	df_ERCMaxChg %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						ERC_PR_chg5yMax_q90 = quantile(ERC_PR_chg5yMax, 0.90),
						ERC_PR_chg5yMax_q75 = quantile(ERC_PR_chg5yMax, 0.75),
						ERC_PR_chg5yMax_q50 = quantile(ERC_PR_chg5yMax, 0.50),
						ERC_PR_chg5yMax_q25 = quantile(ERC_PR_chg5yMax, 0.25),
						ERC_PR_chg5yMax_q10 = quantile(ERC_PR_chg5yMax, 0.1)
						)
# df_ERCMaxChg_qtile


# Proability of ERC rate rising by more than 5% in 40 years
```



## Overall cost reduction effect


**Cost Q1, Measure 1**: Present value of ERC over 40 years compared to baseline (sim-to-sim): differences at PV ERC percentiles of baseline

Calculation:

- Adjust all values with the median PV ERC in baseline normalized to 100. 
- Calculate the difference in PV ERC between baseline and risk-sharing policies for each of the 2000 simulations.
- Find the sims corresponding to the PV ERC of baseline at 5 percentiles: 90, 75, 50, 25, 10. 
- Present the PVC differences of the sims above. 
- The differences are presented in (normalized) dollar values (second table below) and percentages (third table below) 


```{r, warning=FALSE, echo = FALSE}
# Try three different ways to present the differences in PVC

# # 1. PVC with median result of baseline normalized to 100
# df_PVC_sim2sim %>% 
# 	mutate_at(vars(-var, -Percentile), ~ 100 * . / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"]) %>% 
# 	select(var, Percentile, one_of(runnames_show1)) %>% 
# 	kable(digits = 1, caption = "Normalized PV ERC", format = "pandoc")
# 
# # 2. Based on 1, show dollar difference compared to baseline in the same row
# df_PVC_sim2sim %>% 
# 	mutate_at(vars(-var, -Percentile), ~ 100 * . / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"]) %>% 
# 	mutate_at(vars(-var, -Percentile, -baseline), ~  . - baseline) %>% 
# 	select(var, Percentile, one_of(runnames_show1)) %>% 
# 	kable(digits = 1, caption = "Dollar difference from the baseline in the same row", format = "pandoc")

	
# 3. Percentage difference compared to baseline in the same row
# df_PVC_sim2sim %>% 
# 	mutate_at(vars(-var, -Percentile), ~ 100 * . / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"]) %>% 
# 	mutate_at(vars(-var, -Percentile, -baseline), ~  100*(./baseline - 1)) %>% 
# 	select(var, Percentile, one_of(runnames_show1)) %>% 
# 	kable(digits = 1, caption = "Percentage difference from the baseline in the same row (%)", format = "pandoc")

x <- 
df_PVC_sim2sim %>% 
	mutate_at(vars(-var, -Percentile), ~ 100 * . / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"]) %>% 
	mutate_at(vars(-var, -Percentile, -baseline), ~  100*(./baseline - 1)) %>% 
	select(var, Percentile, one_of(runnames_show1)) %>% 
	gt() %>% 
	fmt_number(
    columns = 3:7,
    decimals = 1) %>% 
	tab_header(
    title = "Percentage difference from the baseline in the same row (%)"
  )
x


```


**Cost Q1, Measure 2 [MFC]**: Present value of ERC over 40 years compared to baseline: median differences in 5 return groups

Values in measure 1 are from single simulation runs, which may lead to irregular results due to randomness (the irregularity may be reduced when the number of sims increases). For measure 2, sims are divided into 5 groups by 40-year compound annual return, then we compare the median/mean differences in PV ERC in each group. Note that other grouping methods for sims may give difference results.    

The give groups and their ranges of compound average return are

- Group1: Lower than 20th percentile (`r round(grpVals_CAGR40_vector[5], 4)*100`%)
- Group2: 20th to 40th percentile (`r round(grpVals_CAGR40_vector[5], 4)*100`% to `r round(grpVals_CAGR40_vector[4], 4)*100`%)
- Group3: 40th to 60th percentile (`r round(grpVals_CAGR40_vector[4], 4)*100`% to `r round(grpVals_CAGR40_vector[2], 4)*100`%)
- Group4: 60th to 90th percentile (`r round(grpVals_CAGR40_vector[2], 4)*100`% to `r round(grpVals_CAGR40_vector[1], 4)*100`%)
- Group5: higher than 80th percentile (`r round(grpVals_CAGR40_vector[1], 4)*100`%)


```{r, warning=FALSE, echo = FALSE}
# Alternative measure: PVC differences in 5 CAGR groups 

df_PVC_sim2sim2 <-
	df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	left_join(filter(df_PVC, runname == "baseline") %>% ungroup %>% select(sim, ERC_PV_baseline = ERC_PV), by = "sim" ) %>% 
  left_join(df_CAGR40, by = "sim") %>% 
	mutate(ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
				 ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     ERC_PV_diff     = ERC_PV - ERC_PV_baseline,
				 ERC_PV_diff_pct = 100*( ERC_PV / ERC_PV_baseline - 1)
				 )

fun_sum <- median
# fun_sum <- mean

df_PVC_sim2sim2 %<>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PV          = fun_sum(ERC_PV),
						ERC_PV_diff     = fun_sum(ERC_PV_diff),
						ERC_PV_diff_pct = fun_sum(ERC_PV_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR40))


# 
# df_PVC_sim2sim2 %>% 
# 	select(runname, grp_CAGR40 , ERC_PV) %>% 
# 	spread(runname, ERC_PV) %>% 
# 	select(grp_CAGR40, one_of(runnames_show1)) %>% 
# 	kable(digits = 1, caption = "Median normalized PV ERC by return group", format = "pandoc")
#   
# 
# 
# df_PVC_sim2sim2 %>% 
# 	select(runname, grp_CAGR40 , ERC_PV_diff) %>% 
# 	spread(runname, ERC_PV_diff) %>% 
# 	select(grp_CAGR40, one_of(runnames_show1)) %>% 
#   kable(digits = 1, caption = "Median dollar difference from baseline by return group", format = "pandoc")



df_PVC_sim2sim2 %>% 
	select(runname, grp_CAGR40 , ERC_PV_diff_pct) %>% 
	spread(runname, ERC_PV_diff_pct) %>% 
	select(grp_CAGR40, one_of(runnames_show1)) %>% 
	left_join(df_PVC_sim2sim2 %>%  # adding median baseline PV ERC in each group
							filter(runname == "baseline") %>% 
							ungroup() %>% 
							select(grp_CAGR40, ERC_PV_baseline = ERC_PV), 
						by = "grp_CAGR40") %>% 
	select(grp_CAGR40, ERC_PV_baseline, everything(), -baseline) %>% 
	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("ERC_PV_baseline", runnames_show1),
												         labels = c("PV employer cost\nin Baseline", runnames_show1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = "grp_CAGR40") %>% 
	fmt_number(
    columns = 3:7,
    decimals = 1) %>% 
	tab_header(
    title = "Median percentage differences from baseline by long-term return group (%)"
  ) %>% 
	tab_stubhead(label = "Group")




```


**Cost Q1, Measure 3** Distribution of differences from baseline PV ERC WITHIN each policy

```{r, warning=FALSE, echo = FALSE}


# 3. Percentage difference compared to baseline in the same row
df_PVC_sim2sim_m3 %>% 
	select(Percentile, one_of(runnames_show1)) %>% 
	kable(digits = 1, caption = "Percentiles of % differences from baseline PV ERC within each policy ", format = "pandoc")


```



**Cost Q1, Measure 4 [MFC]** Distribution of PV ERC within each policy

TODO: use box plot 

```{r, warning=FALSE, echo = FALSE}


df_PVC_qtiles %>% 
	mutate_at(vars(-runname,-runname_wlabel), ~ 100 * . / df_PVC_qtiles$ERC_PV_q50[df_PVC_qtiles$runname == "baseline"]) %>% 
	select(runname, contains("ERC_PV")) %>% 
	filter(runname %in% runnames_show1) %>% 
	mutate(runname = factor(runname, levels = runnames_show1)) %>% 
	gather(Percentile, value, -runname) %>% 
	mutate(Percentile = factor(Percentile) %>% fct_inorder()) %>% 
	spread(runname, value) %>% 
	kable(digits = 1, caption = "Percentiles of normalized PV ERC within each policy", format = "pandoc")


fig_title    <- "Distributions of the present value 40-year employer contribution \nunder different COLA policies"
df_PVC_qtiles_plot <- 
  df_PVC_qtiles %>% 
	mutate_at(vars(-runname,-runname_wlabel), ~ 100 * . / df_PVC_qtiles$ERC_PV_q50[df_PVC_qtiles$runname == "baseline"]) %>% 
	select(runname, contains("ERC_PV")) %>% 
	filter(runname %in% runnames_show1) %>% 
	mutate(runname = factor(runname, levels = runnames_show1)) 
  
  df_PVC_qtiles_plot %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = ERC_PV_q10,
							 	 	lower   = ERC_PV_q25,
							 		middle  = ERC_PV_q50,
							 		upper   = ERC_PV_q75,
							 		ymax    = ERC_PV_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 170)) + 
	scale_y_continuous(breaks = seq(0, 300, 20)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of ERC")
	

```




## Dampening effects on contribution volatility

**Cost Q2, Measure 1 [MFC]** Measures the likelihood of large increases in ERC: Probability of ERC rate rising by more than 10 percentage points within 5 years. 

Use table instead of the graph in the paper

```{r echo = FALSE}

df_ERC_hike <-  
  results_stch_FR75 %>% 
	as_tibble() %>% 
	select(runname, sim, year, ERC_PR) %>% 
	group_by(runname, sim) %>% 
	mutate(ERC_hike = cumany( ERC_PR - lag(ERC_PR, 5, Inf) > 0.1) ) %>% 
	group_by(runname, year) %>% 
	summarise(ERC_hike = sum(ERC_hike)/n())

fig_title <- "Probability of ERC rate rising more than 10% \nwithin 5 years up to the given year"
df_ERC_hike %>% 
	filter(runname %in% runnames_show1) %>% 
	ggplot(aes(x = year, y = ERC_hike, color = runname)) +  
	geom_line() +
	geom_point() + 
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(6) )) + 
	scale_y_continuous(labels = function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 x = "Year",
			 y = "Probability",
			 color = "Policy"
			 )


df_ERC_hike %>% 
	filter(runname %in% runnames_show1, year %in% c(10, 20)) %>% 
	spread(runname, ERC_hike) %>% 
	# kable(digits = 2, caption = "Probability of ERC rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", format = "pandoc")
	gather(policy, value, -year) %>% 
	
  mutate(policy = factor(policy, levels = c(runnames_show1),
												         labels = c(runnames_show1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = c("year")) %>% 
	fmt_percent(
    columns = 2:6,
    decimals = 1) %>% 
	tab_header(
    title = "Probability of employer contribution rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years"
  ) %>% 
	tab_stubhead(label = "Up to year")


	
```

**Cost Q2, Measure 2 [MFC]** Measures to what extent risk-sharing policies can buffer the impact of asset shock occurs: Max increase in ERC rate in 5 years.  

Try construct a version of measure 2 in the 5-group format (same row corresponds to same grp)

Possible choice of grouping variable:

  - [MFC]40-year compound return. The same as Q1, easier for the readers, but may not the best one to capture volatility
  - Measure of overall volatility: eg. standard deviation
  - Measure of asset shock[Later]: lowest 3- or 5-year geometric return, then look at the ERC increase associated with the shock, or just the max 5-year change
  

```{r echo= FALSE}
# Table of max increase in ERC rate in 5 years
tab_ERCMaxChg_qtiles <- 
df_ERCMaxChg_qtile %>% 
	select(-runname_wlabel) %>% 
	gather(qtile, value, -runname) %>% 
	mutate(qtile = factor(qtile) %>% fct_inorder()) %>% 
	# mutate(value = 100 * value / value[runname == "baseline" & qtile == "ERC_PV_q50"]) %>% 
	spread(runname, value)

## Explore results for all policies
# tab_ERCMaxChg_qtiles %>% kable(digits = 2)

tab_ERCMaxChg_qtiles %>% 
	select(qtile, one_of(runnames_show1)) %>% 
	knitr::kable(digits = 2, caption = "Max 5-year ERC change, FR=75%", format = 'pandoc')

# Notes:
#  - why does cola_return policy have the lowest compound COLA but does not have the largest cost reduction effect? 

```



```{r echo= FALSE}


fun_sum <- median
# fun_sum <- mean

df_ERCMaxChg %>% 
	select(runname, sim, ERC_PR_chg5yMax) %>% 
	mutate(ERC_PR_chg5yMax = 100 * ERC_PR_chg5yMax) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PR_chg5yMax_med = fun_sum(ERC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_CAGR40)) %>% 
	filter(runname %in% runnames_show1) %>% 
	spread(runname, ERC_PR_chg5yMax_med) %>% 
	# kable(digits = 1, caption = "Max 5-year ERC change in 40-year CAGR groups, starting FR=75%", format = 'pandoc')
	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c(runnames_show1),
												         labels = c(runnames_show1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = c("grp_CAGR40")) %>% 
	fmt_number(
    columns = 3:7,
    decimals = 1) %>% 
	tab_header(
    title = "Maximum increase in employer contribution rate in 5 years by return group (%)"
  ) %>% 
	tab_stubhead(label = "Group")






df_ERCMaxChg %>% 
	select(runname, sim, ERC_PR_chg5yMax) %>% 
	mutate(ERC_PR_chg5yMax = 100 * ERC_PR_chg5yMax) %>% 
	left_join(df_SD_return, by = "sim") %>% 
	group_by(runname, grp_SD_return) %>% 
	summarise(ERC_PR_chg5yMax_med = fun_sum(ERC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_SD_return)) %>% 
	filter(runname %in% runnames_show1) %>% 
	spread(runname, ERC_PR_chg5yMax_med) %>% 
	kable(digits = 1, caption = "Max 5-year ERC change in return volatility (SD) groups, starting FR=75%", format = 'pandoc')


```







**Cost Q2, Measure 3** Measure based on sim-to-sim comparison of ERC rate between baseline and risk-sharing policies. 

TODO: add ERC rate in baseline corresponding to each diff_ERCrate percentiles

```{r sim2sim_prep, echo=FALSE, warning=FALSE}
### EXPLORE

## "sim-to-sim" comparison 
df_bySim_FR75 <- 
	left_join(results_stch_FR75 %>% 
							select(runname, runname_wlabel, sim, year, policy_type, ERC, ERC_PR, EEC, EEC_PR, UAAL),
						results_stch_FR75 %>% 
							ungroup %>% 
							filter(runname == "baseline") %>% 
							select(sim, year, ERC_baseline = ERC, 
										            ERC_PR_baseline = ERC_PR,
										            EEC_baseline = EEC, 
										            EEC_PR_baseline = EEC_PR,
										            UAAL_baseline   = UAAL),
						by = c("sim", "year")
	) %>% 
	filter(runname != "cola_baseline") %>% 
	mutate(ERC_PR_diffBySim = ERC_PR - ERC_PR_baseline,
				 ERC_diffBySim    = ERC - ERC_baseline,
				 EEC_PR_diffBySim = EEC_PR - EEC_PR_baseline,
				 EEC_diffBySim    = EEC - EEC_baseline
				 ) 


# **Sim-to-sim compariosn 1**: quantile differences across all sims and years, difference in ERC rate
tab_bySim_ERCptiles <- 
df_bySim_FR75 %>% 
	filter(runname != "baseline") %>% 
	group_by(runname) %>% 
	summarise(diff_ERCrate_90 = quantile(ERC_PR_diffBySim, 0.90),
						diff_ERCrate_75 = quantile(ERC_PR_diffBySim, 0.75),
						diff_ERCrate_50 = quantile(ERC_PR_diffBySim, 0.50),
						diff_ERCrate_25 = quantile(ERC_PR_diffBySim, 0.25),
						diff_ERCrate_10 = quantile(ERC_PR_diffBySim, 0.10)
						) %>% 
	gather(ptile, values, -runname) %>% 
	mutate(ptile = factor(ptile) %>% fct_inorder()) %>% 
	spread(runname, values)


tab_bySim_ERCptiles %>% 
	select(ptile, one_of(runnames_show1)) %>%  
	mutate_at(vars(-ptile), ~.*100) %>% 
	kable(digits = 2, caption = "Sim-to-sim differences of ERC rate across all sim-year observations (%), FR=75%", format = 'pandoc')
	
```


**Other measures**

- Deterministic asset shock scenario: will help policymakers understand the effect of risk-sharing policies in context. Also serves as a deterministic version of measure2 above.   








## Impact of policy parameters (TODO)

```{r eval=FALSE, include=FALSE}
### EXPLORE

## Make tables for draft paper

# Table for PV ERC, w/o final UAAL
tab_PVERC_qtiles <- 
df_PVC_qtiles %>% 
	select(runname, contains("ERC_PV")) %>% 
	gather(qtile, value, -runname) %>% 
	mutate(qtile = factor(qtile) %>% fct_inorder()) %>% 
	mutate(value = 100 * value / value[runname == "baseline" & qtile == "ERC_PV_q50"]) %>% 
	spread(runname, value)

# tab_PVERC_qtiles %>% kable(digits = 1)

tab_PVERC_qtiles %>% select(qtile, one_of(policy_select)) %>% knitr::kable(digits = 1, caption = "PV ERC, FR=75%", format = 'pandoc')
```

```{r sim2sim_2, eval=FALSE, include=FALSE}
### EXPLORE
# **Sim-to-sim compariosn 2**: Dividing simulations into 5 groups based 40-year CAGR, difference in ERC rate:

# 2. Dividing simulations into 5 groups based 40-year CAGR, difference in ERC rate:
#    1) 90th percentile and above []
#    2) 75th~90th percentile [)
#    3) 25th~75th percentile [)
#    4) 25th percentile and below [)
# Grouping can be done based on other variables (e.g. std of return)

df_CAGR40 <- 
results_all %>% 
	filter(runname == "baseline", sim >= 1) %>% 
	group_by(sim) %>% 
	summarise(CAGR40 = get_geoReturn(i.r)) 
  #summarise(CAGR40 = sd(i.r)) 

grpVals_CAGR40 <-
	df_CAGR40 %>% 
	summarise(CAGR40_q90 = quantile(CAGR40, 0.90),
						CAGR40_q75 = quantile(CAGR40, 0.75),
						CAGR40_q50 = quantile(CAGR40, 0.50),
						CAGR40_q25 = quantile(CAGR40, 0.25),
						CAGR40_q10 = quantile(CAGR40, 0.10)
	) 

grpVals_CAGR40

df_CAGR40 %<>% 
	mutate(grp_CAGR40 = case_when(
		CAGR40 >= grpVals_CAGR40$CAGR40_q90 ~ 1,
		CAGR40 >= grpVals_CAGR40$CAGR40_q75 & CAGR40 < grpVals_CAGR40$CAGR40_q90 ~ 2,
		CAGR40 >= grpVals_CAGR40$CAGR40_q25 & CAGR40 < grpVals_CAGR40$CAGR40_q75 ~ 3,
		CAGR40 >= grpVals_CAGR40$CAGR40_q10 & CAGR40 < grpVals_CAGR40$CAGR40_q25 ~ 4,
		CAGR40 < grpVals_CAGR40$CAGR40_q10 ~ 5,
		TRUE ~ NA_real_) 
	)

	
	
df <- 
df_bySim_FR75 %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	# mutate(grp_CAGR40 = case_when(
	# 	CAGR40 >= grpVals_CAGR40$CAGR40_q90 ~ 1,
	# 	CAGR40 >= grpVals_CAGR40$CAGR40_q75 & CAGR40 < grpVals_CAGR40$CAGR40_q90 ~ 2,
	# 	CAGR40 >= grpVals_CAGR40$CAGR40_q25 & CAGR40 < grpVals_CAGR40$CAGR40_q75 ~ 3,
	# 	CAGR40 >= grpVals_CAGR40$CAGR40_q10 & CAGR40 < grpVals_CAGR40$CAGR40_q25 ~ 4,
	# 	CAGR40 < grpVals_CAGR40$CAGR40_q10 ~ 5,
	# 	TRUE ~ NA_real_) 
	# 	) %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(diff_ERCrate_avg     = mean(ERC_PR_diffBySim, na.rm = TRUE),
						ERCrate_baseline_avg = mean(ERC_PR_baseline, na.rm = TRUE))
# df


df %>%  
	filter(runname != "baseline") %>% 
	ggplot(aes(x = grp_CAGR40, y = diff_ERCrate_avg, color = runname, shape = runname)) + theme_yy() +
	geom_line()+
	geom_point()


tab_bySim_ERCgrp <- 
df %>% spread(runname, diff_ERCrate_avg)


tab_bySim_ERCgrp %>% knitr::kable(digits = 4)



```



# Analysis of Benefits


**Q1. Impact on the overall benefit level (protection against inflation; focus on total PV benefit)**

**Question:** To what extent would contingent COLA policies weaken the (overall) protection against inflation?

COLA is intended to provide protection against inflation. Even for plans with fixed COLA, few of them provide full protection against inflation (usually fraction of CPI) Contingent COLA policies can even further weaken the inflation protection: lower average COLA; same average COLA but weaker protection in bad scenarios (uncertainty in the strength of protection).

**Measures:**

- Show distribution of 40-year compound COLA

1. Two probability based measures for the risk of low overall benefit:
	- 1.1[MFC] Risk of actual overall benefit significantly lower than expected(baseline): Prob of PV benefit is below 90% of PV benefit under baseline
	- 1.2 Risk of failing to protect against inflation, Measure: Prob of PV benefit is below 90% of PV benefit with full inflation protection



2. (TODO) sim-to-sim comparison of PVB: (3 general ways to compare PV-type results)
 - 2.1 differences from baseline at quantiles of baseline PVB (can also be grouped)
 - 2.2* [MFC] median differences in long-term return groups
 - 2.3 percentiles of differences from baseline PVB 

3.*(?) Distribution of overall benefit level: PV (discount only or + attribution ) Benefit for age 60-100: compared to full projection. The PV values may not be staightforward to understand, but is good to have as a measure for overall benefit. It is also easier to see the tail risk here: how low the PV benefit (campared to full inflation protection or baseline) 

**Key results**

 - The probabilities of of total PVB lower than 90% of the baseline level are generally very low. 
 
 - [summary of results from sim-to-sim comparisons]
 
 - For the FR-based cola policies, the starting funded ratio and the design of ramp can have big impact on the results.   


**Discussion**
 - The choice of discount rate for the calculation of PVB: does it make sense to heavily discount benefits at higher ages? Discounting with the survival rate at each age makes sense because it is less likely for retirees to receive benefits at higher ages so those benefits values less to them upon retirement. But it may not make sense to use the return assumption of 7% as the discount rate, because discounting benefit actually reflect individual's time preference of consumption. May make more sense to discount factor in discounted utility function.[check values commonly used in macro models.]
 - If a lower discount rate is used, the differences from the baseline PVB will become larger. (b/c differences accumulate over time)
 

Article on discouting future benefits and costs: https://www.epa.gov/sites/production/files/2017-09/documents/ee-0568-06.pdf


**Q2. Impact on the stability of retirement income (focus on the variability of annual benefit)**

**Question:** Would contingent COLA policies lead to declines in real benefit that may affect retirees welfare? (Related to Q1 but broader)
DB plans are intended to provide secured retirement income. But contingent COLA policies create uncertainty in the benefit payments. The policies may cause deteriorated standard-of-living if retirees experience large declines in real benefit payments that may force them to change their consumption behavior.

**Measures:**

1. Measures for the risk of experiencing low benefit sometime during retirement
	- 1.1 [MFC, to table] Chance of experiencing low benefit at some point: Prob of real benefits falling below 90% of starting benefit in any year up to a given year
	- 1.2 Percentiles of the lowest annual real benefit level in 40 years (pick the lowest real B in each sim, then construct the distribution across all sims)  

2. Measures for large decline of benefit in a short period of time
	- 2.1 Chance of sharp decline of real benefit: Prob of real benefits falling by 10% of starting benefit in any year up to a given year
	- 2.2 [MFC, with return grps]Percentiles of max (or 95th ptile) decrease in real benefit in 5-years for a single cohort: percentiles (Tail-risks)

3. [MFC, with return grps]Range of real benefit level at age 80. Supplemental to other measures. Easier to see the tail risk: how low the real benefit can become (10th percentile)?


**Key results**

- measure 1.1: Very high probability (50%+) of benefit falling below 90% of starting benefit when starting with 75% funded ratio. The probabilities are significantly lower with 100% starting FR. 

- Measure 1.2 Retirees may experience much lower level of benefits under cola_return and cola_FR policies, even in median cases. FR ramp and 100% starting FR can have big impact.  


**Additional question:** How would the initial funded ratio affect the impact of COLA policies contingent upon funded ratio?


Note: Both interest rate (discount rate) and mortality are taken into account in the calculation of PV




```{r benefit_prep, include = FALSE}

# Cohorts to examine:
	# Cohort 1: Retired at age 60 in year 1 (1 - 41)
	# Cohort 2: Retired at age 60 in year 15 (15- 55)
		#  - After the 15-year amortization period for the year-1 UAAL 

# Normalize the benefit at age 60 to 100. 
# Need qxm.r in decrement table 

load("Inputs/riskShaing_demographics_100y.RData")

## Create a model run with cola_actual = infl and append to results_all

df_colaFull <- 
  results_all %>% 
	filter(runname == "baseline") %>% 
	mutate(cola_actual = infl,
				 runname     = "cola_full")

df_benefit_y1 <- 
	bind_rows(results_all, df_colaFull) %>% 
	filter(sim >= 1, year %in% 1:41) %>% 
	select(runname, runname_wlabel, policy_type, sim, year, cola_actual) %>% 
	group_by(runname, sim) %>% 
	mutate(age = 60:100) %>% 
	left_join(decrement %>% ungroup() %>% filter(ea == min(ea))  %>% select(age, qxm.r) , by = "age") %>% 
	mutate(qxm.r   = ifelse(age == max(age), 1, qxm.r),
				 fct_qxm = ifelse(age == 60, 1, lag(cumprod(1-qxm.r))),
				 fct_dr      = 1/(1 + dr)^(age - 60),
				 fct_dr_low  = 1/(1 + dr_low)^(age - 60),
				 B       = 100 * ifelse(age == 60, 1, lag(cumprod(1+cola_actual))),
				 B_real  = B / (1 + infl)^(age - 60),
				 B_real_chg5y = rollapply(B_real, width = 6, get_nyearMin, fill = NA, align = "right")
				 )
# df_benefit_y1 


df_benefit_qtile_y1 <- 
	df_benefit_y1 %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						B_PV_dr    = sum(B * fct_dr),
						B_PV_tot   = sum(B* fct_dr * fct_qxm),
						B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]		
	) %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						B_PV_dr_q90 = quantile(B_PV_dr, 0.90),
						B_PV_dr_q75 = quantile(B_PV_dr, 0.75),
						B_PV_dr_q50 = quantile(B_PV_dr, 0.50),
						B_PV_dr_q25 = quantile(B_PV_dr, 0.25),
						B_PV_dr_q10 = quantile(B_PV_dr, 0.1),
						
						B_PV_tot_q90 = quantile(B_PV_tot, 0.90),
						B_PV_tot_q75 = quantile(B_PV_tot, 0.75),
						B_PV_tot_q50 = quantile(B_PV_tot, 0.50),
						B_PV_tot_q25 = quantile(B_PV_tot, 0.25),
						B_PV_tot_q10 = quantile(B_PV_tot, 0.1),
						
						B_real_chg5yMin_q90 = quantile(B_real_chg5yMin, 0.90),
						B_real_chg5yMin_q75 = quantile(B_real_chg5yMin, 0.75),
						B_real_chg5yMin_q50 = quantile(B_real_chg5yMin, 0.50),
						B_real_chg5yMin_q25 = quantile(B_real_chg5yMin, 0.25),
						B_real_chg5yMin_q10 = quantile(B_real_chg5yMin, 0.1),
						
						B_real_age80_q90 = quantile(B_real_age80, 0.90),
						B_real_age80_q75 = quantile(B_real_age80, 0.75),
						B_real_age80_q50 = quantile(B_real_age80, 0.50),
						B_real_age80_q25 = quantile(B_real_age80, 0.25),
						B_real_age80_q10 = quantile(B_real_age80, 0.1)
						)



# runs_benefit <- c("cola_full", "baseline", "cola_return", "cola_FR", "cola_SDRS", "cola_FR_FR100", "cola_SDRS_FR100")
# runs_benefit_lables <- c(
# 	"COLA equal to inflation",
# 	"Baseline \nYear-1 funded ratio 100%",
# 	"Contingent COLA: \nreturn",
# 	"Contingent COLA: \nFunded ratio threshold",
# 	"SDRS",
# 	"Contingent COLA: \nFunded ratio threshold\nYear-1 funded ratio 100%",
# 	"SDRS \nYear-1 funded ratio 100%"
# )
	

# Distribution of 40-year COLA with 75% initial funded ratio
df_cola <- 
	results_all %>% 
	filter(year %in% 1:40) %>% 
	# filter(year %in% 16:55) %>% 
	filter(sim >= 1, str_detect(runname, "cola|baseline") ) %>% 
	group_by(runname, sim) %>%
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg  = prod(1 + cola_actual[-n()])^(1/(n() - 1)) - 1)

df_cola_qtiles <- 
	df_cola %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg_q10 = quantile(cola_avg, 0.1),
						cola_avg_q25 = quantile(cola_avg, 0.25),
						cola_avg_q50 = quantile(cola_avg, 0.50),
						cola_avg_q75 = quantile(cola_avg, 0.75),
						cola_avg_q90 = quantile(cola_avg, 0.90)
						)

```



## Impact on overall benefit level and protection against inflation

**Distribution of 40-year compound COLA**

```{r dist_COLA, fig.width=8, echo = FALSE}

fig_title    <- "Distributions of 40-year compound annual COLA \nunder different COLA policies"
# fig_subtitle <- "Starting funded ratio: 75%"
fig_cola_qtiles_FR75 <- 
	df_cola_qtiles %>% 
	filter(runname %in% runnames_show2) %>% 
	mutate(runname = factor(runname, levels = runnames_show2,
													         labels = runnames_show2_labels)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.0025), labels = percent) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")
fig_cola_qtiles_FR75


```

**Benefit Q1, Measure 1: Two probability based measures for the risk of low overall benefit**:

- 1.1[MFC] Risk of actual overall benefit significantly lower than expected(baseline): Prob of PV benefit is below 90% of PV benefit under baseline
- 1.2 Risk of failing to protect against inflation: Prob of PV benefit is below 90% of PV benefit with full inflation protection

```{r echo=FALSE}

df_benefit_PV <- 
	df_benefit_y1 %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						# B_PV_dr    = sum(B * fct_dr),
						B_PV_tot    = sum(B* fct_dr * fct_qxm),
						B_PV_tot_drLow   = sum(B* fct_dr_low * fct_qxm)
	)

df_low_pvB <- 
df_benefit_PV %>% 
	left_join(filter(df_benefit_PV, runname == "cola_full") %>% 
							ungroup %>%  select(sim, B_PV_tot_full = B_PV_tot), by = "sim") %>% 
  left_join(filter(df_benefit_PV, runname == "baseline") %>% 
  						ungroup %>%  select(sim, B_PV_tot_baseline = B_PV_tot), by = "sim") %>% 
	mutate(dif_full     = B_PV_tot / B_PV_tot_full,
				 dif_baseline = B_PV_tot / B_PV_tot_baseline
				 ) %>% 
	group_by(runname) %>% 
	summarise(Low_pvB_full_pct90     = 100 * sum(dif_full     <= 0.9)/n(),
						Low_pvB_baseline_pct90 = 100 * sum(dif_baseline <= 0.9)/n(),
						
						Low_pvB_full_pct95     = 100 * sum(dif_full     <= 0.95)/n(),
						Low_pvB_baseline_pct95 = 100 * sum(dif_baseline <= 0.95)/n(),
						)


df_low_pvB %>% 
	filter(runname %in% runnames_show2) %>% 
	select(runname, contains("Low_pvB_baseline")) %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	gather(Measure, value, -runname) %>% 
	spread(runname, value) %>% 
	# kable(digits = 1, caption = "Probability (%) of PV benefit below 90%/95% of that in baseline (cola = 1.5%)", format = 'pandoc')
  gather(policy, value, -Measure) %>% 
	mutate(policy = factor(policy, levels = c(runnames_show2),
												         labels = c(runnames_show2_labels)),
				 
				 Measure = factor(Measure, levels = c("Low_pvB_baseline_pct90", "Low_pvB_baseline_pct95"),
				 								           labels = c("Lower than 90% of Baseline", "Lower than 95% of Baseline")
				 								                     ),
				 value = value / 100
												 ) %>% 
	spread(policy, value) %>% 
	select(-Baseline) %>% 
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = c("Measure")) %>% 
	fmt_percent(
    columns = 2:4,
    decimals = 1) %>% 
	tab_header(
    title = "Probability of present value of benefit below 90% or 95% of the level in baseline"
  ) %>% 
	tab_stubhead(label = "Measure")






# df_low_pvB %>%
# 	filter(runname %in% runnames_show2) %>%
# 	select(runname, contains("Low_pvB_full")) %>%
# 	mutate(runname = factor(runname, levels = runnames_show2)) %>%
# 	gather(Measure, value, -runname) %>%
# 	spread(runname, value) %>%
# 	kable(digits = 1, caption = "Probability (%) of PV benefit below 90%/95% of that with full inflation protection(cola = 2%)", format = 'pandoc')








```

**Benefit Q1, Measure 2: Sim-to-Sim comparisons of PV benefit**

2.2 median differences in long-term return groups 

The give groups and their ranges of compound average return are

- Group1: Lower than 10th percentile (`r round(grpVals_CAGR40_vector[5], 4)*100`%)
- Group2: 10th to 25th percentile (`r round(grpVals_CAGR40_vector[5], 4)*100`% to `r round(grpVals_CAGR40_vector[4], 4)*100`%)
- Group3: 25th to 75th percentile (`r round(grpVals_CAGR40_vector[4], 4)*100`% to `r round(grpVals_CAGR40_vector[2], 4)*100`%)
- Group4: 75th to 90th percentile (`r round(grpVals_CAGR40_vector[2], 4)*100`% to `r round(grpVals_CAGR40_vector[1], 4)*100`%)
- Group5: higher than 90th percentile (`r round(grpVals_CAGR40_vector[1], 4)*100`%)

```{r echo = FALSE, warning= FALSE}


df_PVB_sim2sim_grp <- 
  df_benefit_PV %>% 
	select(-runname_wlabel) %>% 
	left_join(filter(df_benefit_PV, runname == "baseline") %>% ungroup %>% 
							select(sim, B_PV_tot_baseline = B_PV_tot, B_PV_tot_drLow_baseline = B_PV_tot_drLow), by = "sim") %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	mutate(
		     #ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
				 #ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     B_PV_tot_diff     = B_PV_tot - B_PV_tot_baseline,
				 B_PV_tot_diff_pct = 100*( B_PV_tot / B_PV_tot_baseline - 1),
				 
				 B_PV_tot_drLow_diff     = B_PV_tot_drLow - B_PV_tot_drLow_baseline,
				 B_PV_tot_drLow_diff_pct = 100*( B_PV_tot_drLow / B_PV_tot_drLow_baseline - 1)
				 )
	
fun_sum <- median
# fun_sum <- mean

df_PVB_sim2sim_grp %<>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_PV_tot          = fun_sum(B_PV_tot),
						B_PV_tot_diff     = fun_sum(B_PV_tot_diff),
						B_PV_tot_diff_pct = fun_sum(B_PV_tot_diff_pct),
						
						B_PV_tot_drLow          = fun_sum(B_PV_tot_drLow),
						B_PV_tot_drLow_diff     = fun_sum(B_PV_tot_drLow_diff),
						B_PV_tot_drLow_diff_pct = fun_sum(B_PV_tot_drLow_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR40))



df_PVB_sim2sim_grp %>% 
	select(runname, grp_CAGR40, B_PV_tot_diff_pct) %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_PV_tot_diff_pct) %>% 
	select(-baseline) %>% 
	left_join(df_PVB_sim2sim_grp %>% 
							filter(runname == "baseline") %>% 
							ungroup() %>% 
	            select(grp_CAGR40, B_PV_tot),
						by = "grp_CAGR40"
						) %>% 
	select(baseline_PVB = B_PV_tot, everything()) %>% 
	# kable(digits = 1, caption = "Median percentage difference from baseline by return group (%), DR = 7.5%", format = 'pandoc')
	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("baseline_PVB", runnames_show2),
												         labels = c("PV benefit\nin Baseline", runnames_show2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = "grp_CAGR40") %>% 
	fmt_number(
    columns = 4:6,
    decimals = 1) %>% 
	fmt_number(
    columns = 3,
    decimals = 0) %>% 
	tab_header(
    title = "Median percentage difference in present value of benefit from baseline by return group (%)"
  ) %>% 
	tab_stubhead(label = "Group")
	
	


# df_PVB_sim2sim_grp %>% 
# 	select(runname, grp_CAGR40, B_PV_tot_drLow_diff_pct) %>% 
# 	filter(runname %in% runnames_show2) %>% 
# 	ungroup() %>% 
# 	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
# 	spread(runname, B_PV_tot_drLow_diff_pct) %>% 
# 	select(-baseline) %>% 
# 	left_join(df_PVB_sim2sim_grp %>% 
# 							filter(runname == "baseline") %>% 
# 							ungroup() %>% 
# 	            select(grp_CAGR40, B_PV_tot_drLow),
# 						by = "grp_CAGR40"
# 						) %>% 
# 	select(baseline_PVB = B_PV_tot_drLow, everything()) %>% 
# 	kable(digits = 1, caption = "Median percentage difference from baseline by return group (%), DR = 3%", format = 'pandoc')


```


**Benefit Q1, Measure 3: Distribution of PV Benefit**

```{r echo = FALSE}

## Q1 measures
  # B_PV total and B_real_age80
  # runs: baseline, cola_return, cola_FR, cola_SDRS, cola_FR100, cola_SDRS_100

tab_benefit1 <- 
df_benefit_qtile_y1 %>% 
	filter(runname %in% c("cola_full", runnames_show2)) %>% 
	select(runname, starts_with("B_PV_tot")) %>% 
	gather(Var, values, -runname) %>%
	mutate(runname = factor(runname, levels=  c("cola_full", runnames_show2)),
		     # Var = factor(Var) %>% fct_inorder(),
				 values = ifelse(str_detect(Var, "B_PV_tot"),  100 * values / values[runname == "baseline" & Var == "B_PV_tot_q50"], values)
	) %>% 
	spread(runname, values) 
tab_benefit1 %>% knitr::kable(digits = 1)

```

## Impact on the stability of retirement income (variability of annual benefit)


**Benefit Q2, Measure 1: Measures for the risk of experiencing low benefit sometime during retirement**

- Chance of experiencing low benefit in certain years: Prob of real benefits falling below 90% of starting benefit in any year up to a given year
- Percentiles of the lowest annual real benefit level in 40 years (pick the lowest real B in each sim, then construct the distribution across all sims)  


```{r, echo = FALSE}

df_B_low <- 
df_benefit_y1 %>% 
	as_tibble() %>% 
	select(runname, runname_wlabel, sim, year, B_real) %>% 
	group_by(runname, sim) %>% 
	mutate(B_lower90 = cumany(B_real < 90)) %>% 
	group_by(runname, year) %>% 
	summarise(B_lower90 = sum(B_lower90) /n())
	

fig_title <- "Probability of real benefit falling below 90% of starting benefit \nin any year up to a given year"
df_B_low %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup %>% 
	mutate(runname = factor(runname, levels= runnames_show2)) %>% 
	ggplot(aes(x = year, y = B_lower90, color = runname)) +  
	geom_line() +
	geom_point() + 
	scale_color_manual(values = c("black", "grey50", brewer_pal(type = "qual", palette = "Paired")(6) )) + 
	scale_y_continuous(labels = function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 x = "Year",
			 y = "Probability",
			 color = "Policy"
			 )


df_B_low %>% 
	filter(runname %in% runnames_show2, year %in% c(10, 20)) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_lower90) %>% 
	# kable(digits = 3, caption = "Probability of real benefit falling below 90% of starting benefit \nin any year up to year 10 and 20", format = "pandoc") %>% 
  gather(policy, value, -year) %>% 
	mutate(policy = factor(policy, levels = c(runnames_show2),
												         labels = c(runnames_show2_labels))
												 ) %>% 
	spread(policy, value) %>% 
	# select(-Baseline) %>% 
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = c("year")) %>% 
	fmt_percent(
    columns = 2:5,
    decimals = 1) %>% 
	tab_header(
    title = "Probability of real benefit falling below 90% of starting benefit \nin any year up to year 10 or 20"
  ) %>% 
	tab_stubhead(label = "Up to year")



df_B_lowest <- 
df_benefit_y1 %>% 
	as_tibble() %>% 
	select(runname, runname_wlabel, sim, year, B_real) %>% 
	group_by(runname, sim) %>% 
	summarise(B_lowest = min(B_real)) %>% 
	summarise(B_lowest_q90 = quantile(B_lowest, 0.9),
						B_lowest_q50 = quantile(B_lowest, 0.5),
						B_lowest_q10 = quantile(B_lowest, 0.1)
						)


df_B_lowest %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup %>%
	mutate(runname = factor(runname, levels= runnames_show2)) %>% 
	gather(Percentile, value, -runname) %>% 
	mutate(Percentile = factor(Percentile) %>% fct_inorder()) %>% 
	spread(runname, value) %>% 
	kable(digits = 1, caption = "Distribution of the lowest annual real benefit level in 40 years (100 in year 1)", format = 'pandoc')
	
	
```




**Benefit Q2, Measure 2: Measures for large decline of benefit in a short period of time**

- Chance of sharp decline of real benefit: Prob of real benefits falling by 8% of starting benefit in any year up to a given year (8% is arbitrary for now)
- Percentiles of max (or 95th ptile) decrease in real benefit in 5-years for a single cohort: percentiles (Tail-risks)



```{r, echo = FALSE}

df_B_drop <- 
df_benefit_y1 %>% 
	as_tibble() %>% 
	select(runname, runname_wlabel, sim, year, B_real) %>% 
	group_by(runname, sim) %>% 
	mutate(B_drop_5 = cumany(B_real - lag(B_real, 5, -Inf) <= -8)) %>% 
	group_by(runname, year) %>% 
	summarise(B_drop_5 = sum(B_drop_5) /n())

# df_B_drop	

fig_title <- "Probability of real benefits falling by 8% of starting benefit \nin any year up to a given year"
df_B_drop %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup %>% 
	mutate(runname = factor(runname, levels= runnames_show2)) %>% 
	ggplot(aes(x = year, y = B_drop_5, color = runname)) +  
	geom_line() +
	geom_point() + 
	scale_color_manual(values = c("black", "grey50", brewer_pal(type = "qual", palette = "Paired")(6) )) + 
	scale_y_continuous(labels = function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 x = "Year",
			 y = "Probability",
			 color = "Policy"
			 )



# Max 5-year benefit change: percentiles within policies
# tab_benefit2 <- 
# df_benefit_qtile_y1 %>% 
# 	filter(runname %in% runnames_show2) %>% 
# 	select(runname, starts_with("B_real_chg5yMin")) %>% 
# 	gather(Var, values, -runname) %>%
# 	mutate(runname = factor(runname, levels= runnames_show2),
# 				 Var = factor(Var) %>% fct_inorder()
# 	) %>% 
# 	spread(runname, values)
# 
# tab_benefit2 %>% 
# 	kable(digits = 2,
# 				caption = "Distribution of max decrease in real benefit in 5-years", 
# 				format = 'pandoc')



# Max 5-year benefit change: return groups

fun_sum <- median

df_benefit_y1 %>% 
  summarise(B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_real_chg5yMin_med = fun_sum(B_real_chg5yMin)) %>% 
	arrange(runname, desc(grp_CAGR40)) %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_real_chg5yMin_med) %>% 
	# kable(digits = 1, caption = "Max 5-year decrease in benefit by 40-year CAGR group, starting FR=75%", format = 'pandoc')

	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("baseline", runnames_show2),
												         labels = c("Baseline", runnames_show2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = "grp_CAGR40") %>% 
	fmt_number(
    columns = 3:6,
    decimals = 1) %>% 
	tab_header(
    title = "Maximum 5-year decrease (%) in annual benefit, meidan by return group "
  ) %>% 
	tab_stubhead(label = "Group")



	
	
# # Probability of benefit falling below 90% of starting benefit
# df_benefit_probLowBen <- 
# df_benefit_y1 %>% 
# 	filter(runname %in% setdiff(runs_benefit,c("baseline", "cola_full"))) %>% 
# 	ungroup() %>% 
# 	mutate(runname = factor(runname, levels = runs_benefit, labels = runs_benefit_lables)) %>% 
# 	group_by(runname, sim) %>% 
# 	mutate(B_real_low = cumany(B_real <= 90)) %>% 
# 	group_by(runname, year) %>% 
# 	summarise(B_real_low = sum(B_real_low)/n()) 
# 
# 
# fig_title <- "Probability of inflation-adjusted benefit falling below 90% of the year-1 value\n at anytime up ot the given year"
# fig_benefit_probLowBen <- 
# df_benefit_probLowBen %>% 
# 	ggplot(aes(y = B_real_low, x = year, color = runname, shape = runname)) + theme_yy() +
# 	geom_line() + 
# 	geom_point() + 
# 	scale_y_continuous(labels = percent) +
# 	# scale_color_viridis_d(option = "D", begin = 0.3) + 
# 	scale_color_brewer(type = "qual", palette = 3)+
# 	labs(title = fig_title,
# 			 x = "Year",
# 			 y = "Probability",
# 		   color = NULL,
# 			 shape = NULL) +
# 	guides(color = guide_legend(keywidth = 1.5, keyheight = 3))
# fig_benefit_probLowBen
# 
# save_figure(fig_benefit_probLowBen, dir_outputs, w = 9, h = 6 )

```



**Range of real benefit level at age 80**. Supplemental to other measures. Easier to see the tail risk: how low the real benefit can become (10th percentile)?

```{r echo = FALSE}

## Q1 measures
  # B_PV total and B_real_age80
  # runs: baseline, cola_return, cola_FR, cola_SDRS, cola_FR100, cola_SDRS_100

# tab_benefit_age80 <- 
# df_benefit_qtile_y1 %>% 
# 	filter(runname %in% c("cola_full", runnames_show2)) %>% 
# 	select(runname, starts_with("B_real_age80")) %>% 
# 	gather(Var, values, -runname) %>%
# 	mutate(runname = factor(runname, levels=  c("cola_full", runnames_show2)),
# 		     Var = factor(Var) %>% fct_inorder(),
# 	) %>% 
# 	spread(runname, values) 
# tab_benefit_age80 %>% knitr::kable(digits = 1)
# 


fun_sum <- median

df_benefit_y1 %>% 
  summarise(B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_real_age80_med = fun_sum(B_real_age80)) %>% 
	arrange(runname, desc(grp_CAGR40)) %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_real_age80_med) %>% 
	kable(digits = 1, caption = "Real benefit at age 80 by 40-year CAGR group, starting FR=75%", format = 'pandoc')






```

# Trade-off: approach 1

```{r trade-off plots, echo = FALSE}

## PV ERC vs PV benefit, grp 1 and 3

df_sum_PVC <-
	df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	left_join(filter(df_PVC, runname == "baseline") %>% ungroup %>% select(sim, ERC_PV_baseline = ERC_PV), by = "sim" ) %>% 
  left_join(df_CAGR40, by = "sim") %>% 
	mutate(ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"], 
		     ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     ERC_PV_diff     = ERC_PV - ERC_PV_baseline,
		     ERC_PV_diff_pct = 100*( ERC_PV / ERC_PV_baseline - 1)
				 ) %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PV          = median(ERC_PV),
						ERC_PV_diff     = median(ERC_PV_diff),
						ERC_PV_diff_pct = median(ERC_PV_diff_pct))


df_sum_PVB <- 
  df_benefit_PV %>% 
	select(-runname_wlabel) %>% 
	left_join(filter(df_benefit_PV, runname == "baseline") %>% ungroup %>% 
							select(sim, B_PV_tot_baseline = B_PV_tot, B_PV_tot_drLow_baseline = B_PV_tot_drLow), by = "sim") %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
  mutate(
		     B_PV_tot_diff     = B_PV_tot - B_PV_tot_baseline,
				 B_PV_tot_diff_pct = 100*( B_PV_tot / B_PV_tot_baseline - 1),
				 B_PV_tot_drLow_diff     = B_PV_tot_drLow - B_PV_tot_drLow_baseline,
				 B_PV_tot_drLow_diff_pct = 100*( B_PV_tot_drLow / B_PV_tot_drLow_baseline - 1)
				 ) %>% 
	summarise(B_PV_tot          = median(B_PV_tot),
						B_PV_tot_diff     = fun_sum(B_PV_tot_diff),
						B_PV_tot_diff_pct = fun_sum(B_PV_tot_diff_pct),
						
						B_PV_tot_drLow    = median(B_PV_tot_drLow),
						B_PV_tot_drLow_diff     = fun_sum(B_PV_tot_drLow_diff),
						B_PV_tot_drLow_diff_pct = fun_sum(B_PV_tot_drLow_diff_pct)
						) %>% 
	ungroup() %>% 
	mutate(B_PV_tot       = 100 * B_PV_tot / unique(B_PV_tot[runname == "baseline"]),
				 B_PV_tot_drLow = 100 * B_PV_tot_drLow / unique(B_PV_tot_drLow[runname == "baseline"])
				 ) %>% 
  arrange(runname, desc(grp_CAGR40))


df_sum_comparePV <- 
	left_join(df_sum_PVC, df_sum_PVB, by = c("runname", "grp_CAGR40"))


runnames_show_sum <- c("baseline", "cola_return", "cola_FR", "EEC_return", "EEC_FR")  



df_sum_comparePV %>% 
	filter(runname %in% runnames_show_sum, grp_CAGR40 %in% c(1, 3)) %>% 
	mutate(grp_CAGR40 = factor(grp_CAGR40, levels = c(3,1), labels = c("Medium Return", "Low Return"))) %>% 
	ggplot(aes(x = B_PV_tot_diff_pct, y = -ERC_PV_diff_pct, color = runname)) + 
	facet_grid(.~grp_CAGR40) + 
	geom_point() + 
	scale_color_manual(values = c("grey50", brewer_pal(type = "qual", palette = "Paired")(6))) 
  # coord_cartesian(xlim = c(-7, 1), ylim = c(-4, 6))




## PV ERC vs net PV benefit (PV benefit - FV EEC paid)

# Salary history for ea = 25, normalized to make starting benefit = 100

load("Inputs/riskShaing_demographics_100y.RData")

dr_m1 <- 0.075

## cohort: ea = 25, yos = 0 in year 1, retirement year =  36
df_actives_ea25 <- 
	df_actives %>% 
	filter(ea ==  25, year - (age-ea) == 1) %>% 
	select(ea, age, year, 
				 N = number.a, 
				 salary_indiv = sx, 
				 NCx.r_indiv = NCx.r, 
				 NCx.v_indiv = NCx.v, 
				 ALx.r_indiv = ALx.r, 
				 ALx.v_indiv = ALx.v, 
				 PVFBx.r_indiv = PVFBx.r, 
				 PVFBx.v_indiv = PVFBx.v)
df_actives_ea25

df_retirees_ea25 <- 
  df_retirees %>% filter(ea ==  25, year - (age-ea) == 1, year.retire == 36) %>% 
	select(ea, age, year, 
				 N = number.r, 
				 B.r_indiv = B.r, 
				 PVFBx.r_indiv = ALx.r)

df_ea25 <-  
	bind_rows(df_actives_ea25, 
						df_retirees_ea25) %>% 
	mutate(fct_dec = N /N[year == 1]) %>% 
	mutate_all(list(na2zero)) %>% 
	mutate(salary_indiv_norm = 100 * salary_indiv/ B.r_indiv[age == 60] )
df_ea25


df_ea25_sims <- 
results_all %>% 
	filter(sim >= 0, year %in% 1:76) %>% 
	select(runname, runname_wlabel, year, sim, 
				 EEC_PR_plan = EEC_PR, 
				 i.r,
				 dr) %>% 
	left_join(select(df_ea25, year, age, salary_indiv_norm), by = "year") %>% 
	group_by(runname, sim) %>% 
	mutate(EEC_norm = salary_indiv_norm * EEC_PR_plan)



## value of FV EEC 
df_EEC_PV_ea25 <- 
  df_ea25_sims %>% 
	filter(age <=60) %>% 
	mutate(EEC_PV_return = 0,
				 EEC_PV_return = fnC(EEC_PV_return, EEC_norm, i.r),
				 
				 EEC_PV_dr = 0,
				 EEC_PV_dr     = fnC(EEC_PV_return, EEC_norm, dr)
				 ) %>% 
	filter(age ==  60)
	

# Use runs with FR = 100
df_EEC_PV_ea25 %<>% 
	filter(!str_detect(runname, "FR100")) %>% 
	ungroup() %>% 
	mutate(runname = str_remove(runname, "_FR100"))


# Merge with results

df_sum_PVB_net <- 
  df_benefit_PV %>% 
	select(-runname_wlabel) %>% 
	left_join(df_EEC_PV_ea25 %>% select(runname, sim, EEC_PV_return, EEC_PV_dr), by = c("runname", "sim")) %>% 
	mutate(B_PVtot_net_return = B_PV_tot - EEC_PV_return,
				 B_PVtot_net_dr     = B_PV_tot - EEC_PV_dr)
	
	
df_sum_PVB_net %<>% 	
	left_join(filter(df_sum_PVB_net, runname == "baseline") %>% 
							ungroup %>% 
							select(sim, B_PVtot_net_return_baseline = B_PVtot_net_return, B_PVtot_net_dr_baseline = B_PVtot_net_dr ), by = "sim") %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
  mutate(
		     # B_PV_tot_diff     = B_PV_tot - B_PV_tot_baseline,
				 B_PVtot_net_return_diffpct = 100*( B_PVtot_net_return / B_PVtot_net_return_baseline - 1),
				 B_PVtot_net_dr_diffpct     = 100*( B_PVtot_net_dr / B_PVtot_net_dr_baseline - 1)
				 ) %>% 
	summarise( B_PVtot_net_return = median(B_PVtot_net_return),
						 B_PVtot_net_dr     = median(B_PVtot_net_dr),
		         B_PVtot_net_return_diffpct = median( B_PVtot_net_return_diffpct),
		         B_PVtot_net_dr_diffpct     = median( B_PVtot_net_dr_diffpct)
						) %>% 
	ungroup() %>% 
	mutate(B_PVtot_net_return = 100 * B_PVtot_net_return / unique(B_PVtot_net_return[runname == "baseline"]),
				 B_PVtot_net_dr     = 100 * B_PVtot_net_dr / unique(B_PVtot_net_dr[runname == "baseline"])
				 ) %>% 
  arrange(runname, desc(grp_CAGR40))


## construct the plot
df_sum_PVB 


df_sum_comparePV_net <- 
	left_join(df_sum_PVC, df_sum_PVB_net, by = c("runname", "grp_CAGR40"))


# runnames_show_sum <- c("baseline", "cola_return", "cola_FR", "EEC_return", "EEC_FR")  
# df_sum_comparePV_net %>% 
# 	ungroup %>% 
# 	filter(runname %in% runnames_show_sum, grp_CAGR40 %in% c(1, 3, 5)) %>% 
# 	mutate(grp_CAGR40 = factor(grp_CAGR40, levels = c(5, 3,1), 
# 														 labels = c("High Return \n(above 80th percentile)", 
# 														 					   "Medium Return \n(40th~60th percentile)", 
# 														 					   "Low Return \n(below 20th percentile)")),
# 				 runname = factor(runname, levels = runnames_show_sum)
# 				 ) %>% 
# 	ggplot(aes(x = B_PVtot_net_dr_diffpct, y = -ERC_PV_diff_pct, color = runname)) + 
# 	facet_grid(.~grp_CAGR40) + 
# 	geom_point(size = 4) + 
# 	geom_vline(xintercept = 0, linetype = 2, size = 0.5) + 
# 	geom_hline(yintercept = 0, linetype = 2, size = 0.5) + 
# 	scale_color_manual(values = c("grey50", brewer_pal(type = "qual", palette = "Paired")(6))) +
#   coord_cartesian(xlim = c(-13, 26), ylim = c(-2, 10)) + 
# 	scale_x_continuous(breaks = seq(-100, 100, 5)) + 
# 	scale_y_continuous(breaks = seq(-100, 100, 2)) + 
# 	labs(
# 		color = "Policy",
# 		x = "Changes in PV benefit net of PV member contribution (%) \n compared with baseline",
# 		y = "Reduction in PV employer contribution (%) \n compared with baseline"
# 	)



runnames_show_sum        <- c("baseline", "cola_return", "cola_FR", "EEC_return", "EEC_FR") 
runnames_show_sum_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA:\nreturn",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_FR             = "Contingent EEC:\nFunded ratio"
)

df_sum_comparePV_net %>% 
	ungroup %>% 
	filter(runname %in% runnames_show_sum, grp_CAGR40 %in% c(1, 3, 5)) %>% 
	mutate(grp_CAGR40 = factor(grp_CAGR40, levels = c(5, 3,1), 
														 labels = c("High Return \n(above 80th percentile)", 
														 					   "Medium Return \n(40th~60th percentile)", 
														 					   "Low Return \n(below 20th percentile)")),
				 runname = factor(runname, levels = runnames_show_sum, labels = runnames_show_sum_labels)
				 ) %>% 
	ggplot(aes(x = B_PVtot_net_dr_diffpct, y = -ERC_PV_diff_pct, color = runname, shape = grp_CAGR40)) + 
	geom_point(size = 4, stroke = 1.8) + 
	geom_vline(xintercept = 0, linetype = 2, size = 0.5) + 
	geom_hline(yintercept = 0, linetype = 2, size = 0.5) + 
	coord_cartesian(xlim = c(-15, 16), ylim = c(-2, 10)) + 
	scale_color_manual(values = c("grey50", brewer_pal(type = "qual", palette = "Paired")(6))) +
	scale_shape_manual(values = c(17, 19, 25)) +
	scale_x_continuous(breaks = seq(-100, 100, 5)) + 
	scale_y_continuous(breaks = seq(-100, 100, 2)) + 
	labs(
		color = "Policy",
		shape = "Long-term return group",
		x = "Changes (%) in PV benefit net of PV member contribution \n compared with baseline \n(Positive numbers indicate higher benefits)",
		y = "Reduction (%) in PV employer contribution \n compared with baseline \n(Positive numbers indicate lower contributions)"
	) + 
	guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 
				 )





## Max 5-year ERC rate change vs Max 5-year benefit change 

df_sum_ERCMaxChg <- 
  df_ERCMaxChg %>% 
	select(runname, sim, ERC_PR_chg5yMax) %>% 
	mutate(ERC_PR_chg5yMax = 100 * ERC_PR_chg5yMax) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PR_chg5yMax_med = median(ERC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_CAGR40))


df_sum_BMaxChg <- 
df_benefit_y1 %>% 
  summarise(B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_real_chg5yMin_med = median(B_real_chg5yMin)) %>% 
	arrange(runname, desc(grp_CAGR40))


df_sum_maxChg <- 
	left_join(df_sum_ERCMaxChg, df_sum_BMaxChg) %>% 
	group_by(grp_CAGR40) %>% 
	mutate(ERC_maxChg_diff = ERC_PR_chg5yMax_med - ERC_PR_chg5yMax_med[runname == "baseline"],
				 B_maxChg_diff   = B_real_chg5yMin_med - B_real_chg5yMin_med[runname == "baseline"]
				 ) 
df_sum_maxChg 


runnames_show_sum <- c("baseline", "cola_return", "cola_FR", "EEC_return", "EEC_FR")  
df_sum_maxChg %>% 
	ungroup %>% 
	filter(runname %in% runnames_show_sum, grp_CAGR40 %in% c(1, 3)) %>% 
	mutate(grp_CAGR40 = factor(grp_CAGR40, levels = c(3,1), 
														 labels = c("Medium Return \n(40th~60th percentile)", "Low Return \n(below 20th percentile)")),
				 runname = factor(runname, levels = runnames_show_sum)
				 ) %>% 
	ggplot(aes(x = B_maxChg_diff, y = -ERC_maxChg_diff, color = runname)) + 
	facet_grid(.~grp_CAGR40) + 
	geom_point(size = 4) + 
	#geom_vline(xintercept = 0, linetype = 2, size = 0.5) + 
	#geom_hline(yintercept = 0, linetype = 2, size = 0.5) + 
	scale_color_manual(values = c("grey50", brewer_pal(type = "qual", palette = "Paired")(6))) 
  #coord_cartesian(xlim = c(-13, 20), ylim = c(-2, 10)) + 
	#scale_x_continuous(breaks = seq(-100, 100, 5)) + 
	#scale_y_continuous(breaks = seq(-100, 100, 2)) + 
	# labs(
	# 	color = "Policy",
	# 	x = "Changes in PV benefit net of PV member contribution (%) \n compared with baseline",
	# 	y = "Reduction in PV employer contribution (%) \n compared with baseline"
	# )






```









```{r eval=FALSE, include=FALSE}
# Distribution of 40-year COLA with 75% initial funded ratio
df_cola <- 
	results_all %>% 
	filter(year %in% 1:40) %>% 
	# filter(year %in% 16:55) %>% 
	filter(sim >= 1, str_detect(runname, "cola|baseline") ) %>% 
	group_by(runname, sim) %>%
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg  = prod(1 + cola_actual[-n()])^(1/(n() - 1)) - 1)

df_cola_qtiles <- 
	df_cola %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg_q10 = quantile(cola_avg, 0.1),
						cola_avg_q25 = quantile(cola_avg, 0.25),
						cola_avg_q50 = quantile(cola_avg, 0.50),
						cola_avg_q75 = quantile(cola_avg, 0.75),
						cola_avg_q90 = quantile(cola_avg, 0.90)
						)

df_cola_qtiles_FR75 <- 
	df_cola_qtiles %>% 
	filter(!str_detect(runname, "FR100"))

levels(df_cola_qtiles_FR75$runname_wlabel)[df_cola_qtiles_FR75$runname]

df_cola_qtiles_FR100 <- 
	df_cola_qtiles %>% 
	filter(str_detect(runname, "FR100")) %>% 
	mutate(runname_wlabel = factor(runname, 
																 levels = runname, 
																 labels = levels(df_cola_qtiles_FR75$runname_wlabel)[df_cola_qtiles_FR75$runname])) 
df_cola_qtiles_FR100
```

```{r eval=FALSE, include=FALSE}
fig_title    <- "Distributions of 40-year compound annual COLA \nunder different COLA policies"
fig_subtitle <- "Starting funded ratio: 75%"
fig_cola_qtiles_FR75 <- 
	df_cola_qtiles_FR75 %>% 
	# filter(runname %in% runname_stch) %>% 
	ggplot(aes(x = runname_wlabel)) + theme_yy() + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) +
	geom_hline(yintercept =
						 	filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.0025), labels = percent) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")
fig_cola_qtiles_FR75


fig_title    <- "Distributions of 40-year compound annual COLA \nunder different COLA policies"
fig_subtitle <- "Starting funded ratio: 100%"
fig_cola_qtiles_FR100 <- 
	df_cola_qtiles_FR100 %>% 
	# filter(runname %in% runname_stch) %>% 
	ggplot(aes(x = runname_wlabel)) + theme_yy() + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) +
	geom_hline(yintercept =
						 	filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.0025), labels = percent) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")
fig_cola_qtiles_FR100



# The impact of funded ratio can be very large for FR-based policies: 
#   - The legacy UAAL was largely accrued during the working years of the current retirees,
#   - so making the current retirees bear the cost is consistent with inter-generational equity.
#   - But current retirees will need to bear risk of with all NEW UAALs, which are associated
#   - with all members (active and retired). 
# 
# Return based cola is NOT affected by legacy underfunding.   


save_figure(fig_cola_qtiles_FR75, dir_outputs, w = 8,  h = 5)
save_figure(fig_cola_qtiles_FR100, dir_outputs, w = 8,  h = 5)


# Distribution of 40-year COLA with 100% initial funded ratio



```


```{r}

df_actives_ea25 <- 
	df_actives %>% 
	filter(ea ==  25, year - (age-ea) == 1) %>% 
	select(ea, age, year, 
				 N = number.a, 
				 salary_indiv = sx, 
				 NCx.r_indiv = NCx.r, 
				 NCx.v_indiv = NCx.v, 
				 ALx.r_indiv = ALx.r, 
				 ALx.v_indiv = ALx.v, 
				 PVFBx.r_indiv = PVFBx.r, 
				 PVFBx.v_indiv = PVFBx.v,
				 )
df_actives_ea25

df_retirees_ea25 <- 
  df_retirees %>% filter(ea ==  25, year - (age-ea) == 1, year.retire == 36) %>% 
	select(ea, age, year, 
				 N = number.r, 
				 B.r_indiv = B.r, 
				 PVFBx.r_indiv = ALx.r)

df_ea25 <-  
	bind_rows(df_actives_ea25, 
						df_retirees_ea25) %>% 
	mutate(fct_dec = N /N[year == 1]) %>% 
	mutate_all(list(na2zero)) %>% 
	mutate(salary_indiv_norm = 100 * salary_indiv/ B.r_indiv[age == 60] )
df_ea25

fasyears <- 3
benfactor <- 0.021

df_ea25 %>% 
	select(ea, age, year, sx = salary_indiv) %>% 
	mutate(yos = age - ea,
				 Sx = ifelse(age == min(age), 0, lag(cumsum(sx))),
				 n  = pmin(yos, fasyears),
				 fas= ifelse(yos < fasyears, Sx/n, (Sx - lag(Sx, fasyears))/n), # final average salary
         fas= ifelse(age == min(age), 0, fas),
         Bx = na2zero(benfactor * yos * fas),
				 Bx_pct = Bx / Bx[age ==60]
				 )



   

```




# Trade-off: approach 2

Notes on constructing trade-off figures

- Measures for employer and employee should 
	1. cover the same period of time
	2. be both plan level measures or individual level measures


## 40-year plan level measures  


- Employer measure: Total PV ERC in 40 years

- Employee measure: (Total PV benefit payments - Total PV EEC) in 40 years

- Discouting by discount factor (dr = 7.5%)


```{r trade-off2, echo=FALSE}

results_all %>% head

df_tradeOff2 <- 
  results_all %>% 
	select(runname, sim, year, ERC, B, EEC) %>% 
	filter(sim > 0) %>% 
	group_by(runname, sim) %>% 
	mutate(fct_dr = 1/(1 + 0.075)^(year - 1)) %>% 
	summarise(PV_ERC = sum(ERC * fct_dr),
						PV_B   = sum(B * fct_dr),
						PV_EEC = sum(EEC * fct_dr)
						) %>% 
	mutate(PV_BnetEEC = PV_B - PV_EEC) %>% 
	left_join(df_CAGR40, by = "sim") 


df_tradeOff2_FR75 <- 
  df_tradeOff2 %>%
	filter(!str_detect(runname, "FR100")) %>% 
	left_join(df_tradeOff2 %>% 
							ungroup %>% 
							filter(runname == "baseline") %>% 
							select(sim, 
										 PV_ERC_baseline = PV_ERC,
										 PV_EEC_baseline = PV_EEC,
										 PV_B_baseline   = PV_B,
										 PV_BnetEEC_baseline = PV_BnetEEC),
						by = "sim") %>% 
	mutate(ERC_diff = PV_ERC / PV_ERC_baseline - 1,
				 EEC_diff = PV_EEC / PV_EEC_baseline - 1,
				 B_diff   = PV_B / PV_B_baseline - 1,
				 BnetEEC_diff =  PV_BnetEEC / PV_BnetEEC_baseline - 1) %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_diff = median(ERC_diff),
						EEC_diff = median(EEC_diff),
						B_diff   = median(B_diff),
						BnetEEC_diff = median(BnetEEC_diff)
						)


df_tradeOff2_FR100 <- 
  df_tradeOff2 %>%
	filter(str_detect(runname, "FR100")) %>% 
	left_join(df_tradeOff2 %>% 
							ungroup %>% 
							filter(runname == "baseline_FR100") %>% 
							select(sim, 
										 PV_ERC_baseline = PV_ERC,
										 PV_EEC_baseline = PV_EEC,
										 PV_B_baseline   = PV_B,
										 PV_BnetEEC_baseline = PV_BnetEEC),
						by = "sim") %>% 
	mutate(ERC_diff = PV_ERC / PV_ERC_baseline - 1,
				 EEC_diff = PV_EEC / PV_EEC_baseline - 1,
				 B_diff   = PV_B / PV_B_baseline - 1,
				 BnetEEC_diff =  PV_BnetEEC / PV_BnetEEC_baseline - 1) %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_diff = median(ERC_diff),
						EEC_diff = median(EEC_diff),
						B_diff   = median(B_diff),
						BnetEEC_diff = median(BnetEEC_diff)
						)




runnames_show_sum        <- c("baseline", "cola_return", "cola_FR", "EEC_return", "EEC_FR") 
runnames_show_sum_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA:\nreturn",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_FR             = "Contingent EEC:\nFunded ratio"
)
runnames_show_sum_FR100 <- paste0(runnames_show_sum, "_FR100") 



df_tradeOff2_FR75 %>% 
	filter(runname %in% runnames_show_sum, grp_CAGR40 %in% c(1,3,5)) %>% 
	relocate(runname, grp_CAGR40, ERC_diff, BnetEEC_diff, B_diff ) %>% 
	arrange(grp_CAGR40) %>% 
	mutate(grp_CAGR40 = factor(grp_CAGR40, levels = c(5, 3,1), 
														 labels = c("High Return \n(above 80th percentile)", 
														 					  "Medium Return \n(40th~60th percentile)", 
														 					  "Low Return \n(below 20th percentile)")),
				 runname = factor(runname, levels = runnames_show_sum, labels = runnames_show_sum_labels)
				 ) %>% 
	ggplot(aes(x = BnetEEC_diff, y = ERC_diff, color = runname, shape = grp_CAGR40)) + 
	geom_point(size = 4, stroke = 1.8) + 
	geom_vline(xintercept = 0, linetype = 2, size = 0.5) + 
	geom_hline(yintercept = 0, linetype = 2, size = 0.5) + 
	# coord_cartesian(xlim = c(-15, 16), ylim = c(-2, 10)) + 
	scale_color_manual(values = c("grey50", brewer_pal(type = "qual", palette = "Paired")(6))) +
	scale_shape_manual(values = c(17, 19, 25)) +
	scale_x_continuous(breaks = seq(-1, 1, 0.02), labels = function(x) percent(x, accuracy = 1)) + 
	scale_y_continuous(breaks = seq(-1, 1, 0.02), labels = function(x) percent(x, accuracy = 1)) +
	labs(
		color = "Policy",
		shape = "Long-term return group",
		x = "Total PV benefit net of tota PV member contribution \n compared with baseline",
		y = "Total PV employer contribution \n compared with baseline"
	) + 
	guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )



df_tradeOff2_FR75 %>% 
	filter(runname %in% runnames_show_sum, grp_CAGR40 %in% c(1,3,5)) %>% 
	relocate(runname, grp_CAGR40, ERC_diff, BnetEEC_diff, B_diff ) %>% 
	arrange(grp_CAGR40) %>% 
	mutate(grp_CAGR40 = factor(grp_CAGR40, levels = c(5, 3,1), 
														 labels = c("High Return \n(above 80th percentile)", 
														 					  "Medium Return \n(40th~60th percentile)", 
														 					  "Low Return \n(below 20th percentile)")),
				 runname = factor(runname, levels = runnames_show_sum, labels = runnames_show_sum_labels)
				 ) %>% 
	ggplot(aes(x = BnetEEC_diff, y = ERC_diff, color = runname)) + 
	facet_grid(.~grp_CAGR40) +
	geom_point(size = 4, stroke = 1.8) + 
	geom_vline(xintercept = 0, linetype = 2, size = 0.5) + 
	geom_hline(yintercept = 0, linetype = 2, size = 0.5) + 
	# coord_cartesian(xlim = c(-15, 16), ylim = c(-2, 10)) + 
	scale_color_manual(values = c("grey50", brewer_pal(type = "qual", palette = "Paired")(6))) +
	scale_shape_manual(values = c(17, 19, 25)) +
	scale_x_continuous(breaks = seq(-1, 1, 0.02), labels = function(x) percent(x, accuracy = 1)) + 
	scale_y_continuous(breaks = seq(-1, 1, 0.02), labels = function(x) percent(x, accuracy = 1)) +
	labs(
		color = "Policy",
		shape = "Long-term return group",
		x = "Total PV benefit net of tota PV member contribution \n compared with baseline",
		y = "Total PV employer contribution \n compared with baseline"
	) + 
	guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )













```





## lifetime (age 30-100) individual level measures





# Deterministic asset shock scenario

```{r echo = FALSE}

## Deterministic asset shock scenarios:

# sim -1: starting FR = 100%
# sim -2: starting FR = 75%

df_assetShock <- 
	results_all %>% 
	filter(sim < 0)


runnames_show_det <- c("baseline", 
										
										  "cola_return", 
										  "cola_FR",
											# "cola_FRramp"
							
							        "EEC_return",
										  "EEC_FR"
										  
										  # "EEC_sharedADCfloor"
										  #"hybrid_DB"
										)
runnames_show_det_labels <- c(
	baseline           = "Baseline:\nNo risk-sharing",
	cola_return        = "Contingent COLA:\nReturn",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_FR             = "Contingent EEC:\nFunded ratio"
)



df_assetShock_plot <- 
  df_assetShock %>% 
	filter(sim == -2, year <=30, runname %in% runnames_show_det) %>% # sim -2: 75% starting FR
	mutate(SC_PR = SC / PR) %>% 
	select(runname, sim, year,ERC, ERC_PR, FR_MA, NC_PR, EEC_PR, SC_PR, cola_actual) %>% 
	mutate(runname = factor(runname, runnames_show_det),
				 runname_label = factor(runname, labels = runnames_show_det_labels))

# df_assetShock_plot


# Plotting ERC rate  

fig_title <- "Employer contribution rates after the asset shock\nunder different risk-sharing policies"

fig_shock_ERC1 <- 
  df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(Alpha = ifelse(runname %in% runnames_show_det[(1)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label, alpha = Alpha)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
	annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) +
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) )) +
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) +
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") +
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )
fig_shock_ERC1

fig_shock_ERC2 <- 
df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(alpha = ifelse(runname %in% runnames_show_det[(1:3)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label, alpha = alpha)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
	coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) )) + 
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) + 
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )

fig_shock_ERC3 <- 
df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(alpha = ifelse(!runname %in% runnames_show_det[(2:3)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label, alpha = alpha)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))+
  scale_alpha_continuous(range = c(0.1,1), guide = FALSE) + 
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )

save_figure(fig_shock_ERC1, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)
save_figure(fig_shock_ERC2, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)
save_figure(fig_shock_ERC3, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)

fig_shock_ERC1
fig_shock_ERC2
fig_shock_ERC3



df_assetShock_plot %>% filter(year == 10)


df_assetShock_plot %>% 
	filter(year <=15) %>% 
	group_by(runname) %>% 
	summarise(ERC = sum(ERC / (1 + 0.075)^(year-1))) %>% 
	mutate(ERC_diff = ERC / ERC[runname == "baseline"] - 1 )




# Plotting FR rate  
df_assetShock_plot %>% 
	filter(year <=20) %>% 
	ggplot(aes(x = year, y = FR_MA, color = runname)) +
	geom_line() + 
	geom_point() + 
  coord_cartesian(ylim = c(0.5, 1))	+
	scale_y_continuous(breaks = seq(0, 1, 0.1), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))
# Note that baseline and EEC_FR have the same TOTAL contribution and therefore the same FR. 





load("Inputs/riskShaing_demographics_100y.RData")


df_benefit_det <- 
	results_all %>% 
	filter(sim == -2, year %in% 1:41) %>% 
	select(runname, runname_wlabel, policy_type, sim, year, cola_actual) %>% 
	group_by(runname, sim) %>% 
	mutate(age = 60:100) %>% 
	mutate(
				 B       = 100 * ifelse(age == 60, 1, lag(cumprod(1+cola_actual))),
				 B_real  = B / (1 + infl)^(age - 60)
				 ) %>% 
	filter(runname %in% runnames_show_det, year <= 15) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show_det),
				 runname_label = factor(runname, labels = runnames_show_det_labels))



fig_title <- "Inflation-adjusted annual benefits after the asset shock\nunder different risk-sharing policies"
fig_subtitle <- "Benefit in year 1 = 100"

fig_shock_realB <- 
df_benefit_det %>% 
	filter(runname %in% runnames_show_det[1:3]) %>% 
	ggplot(aes(x = year, y = B_real, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -Inf, ymax = Inf, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -Inf, ymax = Inf, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 105, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 105, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 105, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
	coord_cartesian(ylim = c(60, 107))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 200, 10)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))+
  scale_alpha_continuous(range = c(0.1,1), guide = FALSE) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
		   x = "Year",
			 y = "Real annual benefit ",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )
	
fig_shock_realB
save_figure(fig_shock_realB, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)





## ERC plot for paper


# Plotting ERC rate  

fig_title <- "Employer contribution rates after the asset shock\nunder different risk-sharing policies"

fig_shock_ERCpaper <- 
  df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(Alpha = ifelse(runname %in% runnames_show_det[(1)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
	annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) +
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) )) +
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) +
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") +
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )
fig_shock_ERCpaper


save_figure(fig_shock_ERCpaper, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)





```








# Tables for MFC2020


```{r tab_ERC_PV, echo = FALSE}
df_PVC_sim2sim2 <-
	df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	left_join(filter(df_PVC, runname == "baseline") %>% ungroup %>% select(sim, ERC_PV_baseline = ERC_PV), by = "sim" ) %>% 
  left_join(df_CAGR40, by = "sim") %>% 
	mutate(ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
				 ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     ERC_PV_diff     = ERC_PV - ERC_PV_baseline,
				 ERC_PV_diff_pct = 100*( ERC_PV / ERC_PV_baseline - 1)
				 )

fun_sum <- median
# fun_sum <- mean

df_PVC_sim2sim2 %<>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PV          = fun_sum(ERC_PV),
						ERC_PV_diff     = fun_sum(ERC_PV_diff),
						ERC_PV_diff_pct = fun_sum(ERC_PV_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR40))


df_tab_ERC_PV <- 
df_PVC_sim2sim2 %>% 
	select(runname, grp_CAGR40 , ERC_PV_diff_pct) %>% 
	spread(runname, ERC_PV_diff_pct) %>% 
	select(grp_CAGR40, one_of(runnames_show1)) %>% 
	left_join(df_PVC_sim2sim2 %>%  # adding median baseline PV ERC in each group
							filter(runname == "baseline") %>% 
							ungroup() %>% 
							select(grp_CAGR40, ERC_PV_baseline = ERC_PV), 
						by = "grp_CAGR40") %>% 
	select(grp_CAGR40, ERC_PV_baseline, everything(), -baseline) %>% 
	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("ERC_PV_baseline", runnames_show1),
												         labels = c("PV employer cost\nin Baseline", runnames_show1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything())
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	
tab_ERC_PV <- 
	df_tab_ERC_PV %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV employer contribution\n from baseline by long-term return quintile\n(Median values within groups)", 
								 colwidths = 7) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:7, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:7, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 1) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")

tab_ERC_PV %>% dim_pretty()	
tab_ERC_PV
save_as_image(tab_ERC_PV, path = here::here("Outputs_Analysis/tab_ERC_PV.png"))


tab_ERC_PV_3rows <- 
	df_tab_ERC_PV %>% 
  filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV employer contribution\n from baseline by long-term return quintile\n(Median values within groups)", 
								 colwidths = 7) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:7, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:7, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 1) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")

tab_ERC_PV_3rows
save_as_image(tab_ERC_PV_3rows, path = here::here("Outputs_Analysis/tab_ERC_PV_3rows.png"))


```




```{r tab_ERC_vol1, echo = FALSE}

fun_sum <- median
# fun_sum <- mean

df_tab_ERC_vol1 <- 
df_ERCMaxChg %>% 
	select(runname, sim, ERC_PR_chg5yMax) %>% 
	mutate(ERC_PR_chg5yMax = 100 * ERC_PR_chg5yMax) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PR_chg5yMax_med = fun_sum(ERC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_CAGR40)) %>% 
	filter(runname %in% runnames_show1) %>% 
	spread(runname, ERC_PR_chg5yMax_med) %>% 
	# kable(digits = 1, caption = "Max 5-year ERC change in 40-year CAGR groups, starting FR=75%", format = 'pandoc')
	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c(runnames_show1),
												         labels = c(runnames_show1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) 


tab_ERC_vol1 <- 
  df_tab_ERC_vol1 %>% 
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	flextable() %>%
	add_header_row(values = "Maximum increase in employer contribution rate in 5 years by long-term return quintile\n(Median values within groups)", 
								 colwidths = 7) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:7, width = 1.4) %>% 
	colformat_num(j = 3:7, digits = 1, suffix = "%") 
tab_ERC_vol1


save_as_image(tab_ERC_vol1, path = here::here("Outputs_Analysis/tab_ERC_vol1.png"))


tab_ERC_vol1_3rows <- 
  df_tab_ERC_vol1 %>% 
	filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	flextable() %>%
	add_header_row(values = "Maximum increase in employer contribution rate in 5 years by long-term return quintile\n(Median values within groups)", 
								 colwidths = 7) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:7, width = 1.4) %>% 
	colformat_num(j = 3:7, digits = 1, suffix = "%") 
tab_ERC_vol1_3rows


save_as_image(tab_ERC_vol1_3rows, path = here::here("Outputs_Analysis/tab_ERC_vol1_3rows.png"))

```



```{r tab_ERC_vol2, echo = FALSE}

df_ERC_hike <-  
  results_stch_FR75 %>% 
	as_tibble() %>% 
	select(runname, sim, year, ERC_PR) %>% 
	group_by(runname, sim) %>% 
	mutate(ERC_hike = cumany( ERC_PR - lag(ERC_PR, 5, Inf) > 0.1) ) %>% 
	group_by(runname, year) %>% 
	summarise(ERC_hike = sum(ERC_hike)/n())


tab_ERC_vol2 <- 
df_ERC_hike %>% 
	filter(runname %in% runnames_show1, year %in% c(10, 20)) %>% 
	spread(runname, ERC_hike) %>% 
	# kable(digits = 2, caption = "Probability of ERC rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", format = "pandoc")
	gather(policy, value, -year) %>% 
	
  mutate(policy = factor(policy, levels = c(runnames_show1),
												         labels = c(runnames_show1_labels)),
				 value = value * 100) %>% 
	spread(policy, value) %>% 
	
	flextable() %>%
	add_header_row(values = "Probability of employer contribution rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 1, height = .8) %>%
	height(part = "header", i = 2, height = 1) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2:6, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	colformat_num(j = 2:6, digits = 1, suffix = "%") %>% 
	set_header_labels(year = "Up to year"
									   )
tab_ERC_vol2

save_as_image(tab_ERC_vol2, path = here::here("Outputs_Analysis/tab_ERC_vol2.png"))
	
```





```{r tab_B_PV1, echo=FALSE}

df_benefit_PV <- 
	df_benefit_y1 %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						# B_PV_dr    = sum(B * fct_dr),
						B_PV_tot    = sum(B* fct_dr * fct_qxm),
						B_PV_tot_drLow   = sum(B* fct_dr_low * fct_qxm)
	)


df_PVB_sim2sim_grp <- 
  df_benefit_PV %>% 
	select(-runname_wlabel) %>% 
	left_join(filter(df_benefit_PV, runname == "baseline") %>% ungroup %>% 
							select(sim, B_PV_tot_baseline = B_PV_tot, B_PV_tot_drLow_baseline = B_PV_tot_drLow), by = "sim") %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	mutate(
		     #ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
				 #ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     B_PV_tot_diff     = B_PV_tot - B_PV_tot_baseline,
				 B_PV_tot_diff_pct = 100*( B_PV_tot / B_PV_tot_baseline - 1),
				 
				 B_PV_tot_drLow_diff     = B_PV_tot_drLow - B_PV_tot_drLow_baseline,
				 B_PV_tot_drLow_diff_pct = 100*( B_PV_tot_drLow / B_PV_tot_drLow_baseline - 1)
				 )
	
fun_sum <- median
# fun_sum <- mean

df_PVB_sim2sim_grp %<>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_PV_tot          = fun_sum(B_PV_tot),
						B_PV_tot_diff     = fun_sum(B_PV_tot_diff),
						B_PV_tot_diff_pct = fun_sum(B_PV_tot_diff_pct),
						
						B_PV_tot_drLow          = fun_sum(B_PV_tot_drLow),
						B_PV_tot_drLow_diff     = fun_sum(B_PV_tot_drLow_diff),
						B_PV_tot_drLow_diff_pct = fun_sum(B_PV_tot_drLow_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR40))


df_tab_B_PV1 <- 
df_PVB_sim2sim_grp %>% 
	select(runname, grp_CAGR40, B_PV_tot_diff_pct) %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_PV_tot_diff_pct) %>% 
	select(-baseline) %>% 
	left_join(df_PVB_sim2sim_grp %>% 
							filter(runname == "baseline") %>% 
							ungroup() %>% 
	            select(grp_CAGR40, B_PV_tot),
						by = "grp_CAGR40"
						) %>% 
	select(baseline_PVB = B_PV_tot, everything()) %>% 
	# kable(digits = 1, caption = "Median percentage difference from baseline by return group (%), DR = 7.5%", format = 'pandoc')
	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("baseline_PVB", runnames_show2),
												         labels = c("PV benefit\nin Baseline", runnames_show2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything())
	
tab_B_PV1 <- 
  df_tab_B_PV1 %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV benefit from baseline\nby long-term return quintile\n(Median values within groups)", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:6, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:6, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")

tab_B_PV1
save_as_image(tab_B_PV1, path = here::here("Outputs_Analysis/tab_B_PV1.png"))


tab_B_PV1_3rows <- 
  df_tab_B_PV1 %>% 
	filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV benefit from baseline\nby long-term return quintile\n(Median values within groups)", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:6, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:6, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")

tab_B_PV1_3rows
save_as_image(tab_B_PV1_3rows, path = here::here("Outputs_Analysis/tab_B_PV1_3rows.png"))



```





```{r tab_B_PV2, echo=FALSE}

df_benefit_PV <- 
	df_benefit_y1 %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						# B_PV_dr    = sum(B * fct_dr),
						B_PV_tot    = sum(B* fct_dr * fct_qxm),
						B_PV_tot_drLow   = sum(B* fct_dr_low * fct_qxm)
	)

df_low_pvB <- 
df_benefit_PV %>% 
	left_join(filter(df_benefit_PV, runname == "cola_full") %>% 
							ungroup %>%  select(sim, B_PV_tot_full = B_PV_tot), by = "sim") %>% 
  left_join(filter(df_benefit_PV, runname == "baseline") %>% 
  						ungroup %>%  select(sim, B_PV_tot_baseline = B_PV_tot), by = "sim") %>% 
	mutate(dif_full     = B_PV_tot / B_PV_tot_full,
				 dif_baseline = B_PV_tot / B_PV_tot_baseline
				 ) %>% 
	group_by(runname) %>% 
	summarise(Low_pvB_full_pct90     = 100 * sum(dif_full     <= 0.9)/n(),
						Low_pvB_baseline_pct90 = 100 * sum(dif_baseline <= 0.9)/n(),
						
						Low_pvB_full_pct95     = 100 * sum(dif_full     <= 0.95)/n(),
						Low_pvB_baseline_pct95 = 100 * sum(dif_baseline <= 0.95)/n(),
						)

tab_B_PV2 <- 
df_low_pvB %>% 
	filter(runname %in% runnames_show2) %>% 
	select(runname, contains("Low_pvB_baseline")) %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	gather(Measure, value, -runname) %>% 
	spread(runname, value) %>% 
	# kable(digits = 1, caption = "Probability (%) of PV benefit below 90%/95% of that in baseline (cola = 1.5%)", format = 'pandoc')
  gather(policy, value, -Measure) %>% 
	mutate(policy = factor(policy, levels = c(runnames_show2),
												         labels = c(runnames_show2_labels)),
				 
				 Measure = factor(Measure, levels = c("Low_pvB_baseline_pct90", "Low_pvB_baseline_pct95"),
				 								           labels = c("Lower than 90% of Baseline", "Lower than 95% of Baseline")
				 								                     ),
				 value = value
												 ) %>% 
	spread(policy, value) %>% 
	select(-Baseline) %>% 
  flextable() %>%
	add_header_row(values = "Probability of present value of benefit below 90% or 95% of the level in baseline", 
								 colwidths = 4) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 2) %>%
	width(j = 2:4, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	colformat_num(j = 2:4, digits = 1, suffix = "%") %>% 
	#colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(Measure = "Measure")

tab_B_PV2
	
save_as_image(tab_B_PV2, path = here::here("Outputs_Analysis/tab_B_PV2.png"))

```





```{r tab_B_vol2, echo = FALSE}


fun_sum <- median

df_tab_B_vol1 <- 
df_benefit_y1 %>% 
  summarise(B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_real_chg5yMin_med = fun_sum(B_real_chg5yMin)) %>% 
	arrange(runname, desc(grp_CAGR40)) %>% 
	filter(runname %in% runnames_show2) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_real_chg5yMin_med) %>% 
	# kable(digits = 1, caption = "Max 5-year decrease in benefit by 40-year CAGR group, starting FR=75%", format = 'pandoc')

	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("baseline", runnames_show2),
												         labels = c("Baseline", runnames_show2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) 
	

tab_B_vol1 <-  
	df_tab_B_vol1 %>% 
	flextable() %>%
	add_header_row(values = "Maximum 5-year decreases in real benefit by long-term return quintile\n(Median values within groups)", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:6, width = 1.5) %>% 
	colformat_num(j = 3:6, digits = 1, suffix = "%") 

tab_B_vol1
save_as_image(tab_B_vol1, path = here::here("Outputs_Analysis/tab_B_vol1.png"))



tab_B_vol1_3rows <-  
	df_tab_B_vol1 %>% 
	filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	flextable() %>%
	add_header_row(values = "Maximum 5-year decreases in real benefit by long-term return quintile\n(Median values within groups)", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:6, width = 1.5) %>% 
	colformat_num(j = 3:6, digits = 1, suffix = "%") 

tab_B_vol1_3rows
save_as_image(tab_B_vol1_3rows, path = here::here("Outputs_Analysis/tab_B_vol1_3rows.png"))





```

```{r, tab_B_vol2, echo = FALSE}

df_B_low <- 
df_benefit_y1 %>% 
	as_tibble() %>% 
	select(runname, runname_wlabel, sim, year, B_real) %>% 
	group_by(runname, sim) %>% 
	mutate(B_lower90 = cumany(B_real < 90)) %>% 
	group_by(runname, year) %>% 
	summarise(B_lower90 = sum(B_lower90) /n())


tab_B_vol2 <- 
df_B_low %>% 
	filter(runname %in% runnames_show2, year %in% c(10, 20)) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_lower90) %>% 
	# kable(digits = 3, caption = "Probability of real benefit falling below 90% of starting benefit \nin any year up to year 10 and 20", format = "pandoc") %>% 
  gather(policy, value, -year) %>% 
	mutate(policy = factor(policy, levels = c(runnames_show2),
												         labels = c(runnames_show2_labels)),
				 value = 100 * value
												 ) %>% 
	spread(policy, value) %>% 
	flextable() %>%
	add_header_row(values = "Probability of real benefit falling below 90% \nof starting benefit in any year up to year 10 or 20", 
								 colwidths = 5) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	width(j = 1, width = .8) %>%
	width(j = 2:5, width = 1.5) %>% 
	colformat_num(j = 2:5, digits = 1, suffix = "%") %>% 
	set_header_labels(year = "Up to year") 
tab_B_vol2 	
	

save_as_image(tab_B_vol2, path = here::here("Outputs_Analysis/tab_B_vol2.png"))



```





